\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}


\begin{document}
\section*{The Multiverse}
John and Jane are two characters living in a multiverse.
They have one thing in common amongst every timeline, however.
And what is this one thing in common?
John is a criminal. And Jane is his victim.


John has green eyes, bronze skin, and blond hair.
Jane has green eyes, apricot skin, and gray hair.
Now, the multiverse is a big place. But we are only concerned with one very small part of it {-} the city of Kyyumi{-}Migiwy, jewel of the North{-}East, and where John and Jane live.
This is where, throughout every timeline, John attacks Jane in some way.
On this particular day, the 5th of March, it was warmer than normal and hailing, with a light breeze coming from the North.

\tableofcontents

\subsection{A Timeline In Which John Watches Jane}


He's using a plastic telescope, made in Italy.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her garage window.
John knows Jane's secret. What is her secret? She is a amicussexual mosaigender kiloraccoon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Persuades Jane To Off Herself}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a droning weatherbitten hedge{-}pig?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was precise, Jane thinks.
In fact, the more she appraises his argument, the more she realizes it was almost certainly precise, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 500 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink bits douse the cyan walls, and scarlet fluid pools upon the floor.
\subsection{A Timeline In Which John Agonizes Jane}


John immobilizes Jane, using a specially modified bed, made from steel.
He then gags her, using a ebony spider{-}gag.
John turns on the device, and the lilac electrodes work their magic upon her.
Jane shrieks through her gag, trying to escape.
\subsection{A Timeline In Which John Milks Jane}


John pulls out a letter, encased in a blonde envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} crimsoncoyote347@smail.com {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is dark and grimy, with a disreputable black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see cream walls inside the building.
John steps out of the gloom, catching Jane off{-}guard.
He nudges her with an illegally bought revolver, a Smith \& Wesson Model 340PD.
He commands Jane to give him his money.
Wobbling with fear, she hands him her pochette.
She takes her change and slips away, thankful that she survived.
John receives 242 Emerald Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a plastic telescope, made in Prussia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her bedroom window.
John knows Jane's secret. What is her secret? She is a antihaemosexual digigender quadraskunk, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Robs Jane}


Jane was striding past a dark alley.
It is broken{-}down and ruinous, with a nasty cult hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see blonde walls inside the building.
John steps out of the darkness, surprising Jane.
He prods her with an illegally bought revolver, a Colt Anaconda.
He directs Jane to give him his money.
Wobbling with fear, she hands him her pouch.
She takes her change and escapes, thankful that she survived.
John receives 310 Ivory Crowns, and is pleased with his gain.
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Maltobull is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Maltobull is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a intraromantic bigenderfluid millihorse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Charms Jane}


The apartment has a blonde concrete floor, and the walls are painted crimson.
The bedroom has a rubber bed, with cream violet petals strewn about it.
John wanders to Jane, and kisses her lips.
John parks in her mauve boat.
Jane howls in wicked euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Dupes Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Ken Bankole[cyancat385@chainmail.landica]
\\
I am Doctor Ken Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 17th of March, 1944, my client and his wife and their only daughter were in a car crash on the main road from Lagos to Kaduna (they died).
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 263 tonnes of plastic Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 28\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Ken Bankole
\\\\
Jane thinks that this guy is really ethical, and sends him some money.
John receives 216 Emerald Notes, and is pleased with his gain.
\subsection{A Timeline In Which John Mugs Jane}


Jane was strolling past a dark alley.
It is dirty and drab, with a unpleasant opium den hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see cobalt walls inside the building.
John steps out of the darkness, taking Jane by surprise.
He pokes her with an illegally bought revolver, a Smith \& Wesson Model 340PD.
He directs Jane to give him his money.
Swaying with fear, she hands him her wallet.
She takes her change and runs for it, thankful that she survived.
John receives 254 Indigo Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a aluminium spyglass, made in Australia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her conservatory window.
John knows Jane's secret. What is her secret? She is a objectumsexual anesigender decacoyote, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a forcefield generator, made from titanium.
John strangles Jane.
Her face turns cyan.
\subsection{A Timeline In Which John Cheats Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: URGENT
FROM: Mike Okon[scarletmouse905@tmail.orange]
\\
I am Doctor Mike Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 29th of February, 1973, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 10983 tonnes of hemp Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 31\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Mike Okon
\\\\
Jane thinks that this guy is really responsible, and sends him some money.
John receives 150 Bear Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a frame, made from osmium.
John throttles Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Titillates Jane}


The apartment has a blue concrete floor, and the walls are painted peach.
The bedroom has a titanium bed, with salmon chrysantheum petals strewn about it.
John saunters to Jane, and sucks upon her lips.
John rushes her lilac toothpaste.
Jane shouts in diabolical gratification, and John continues throughout the night...
\subsection{A Timeline In Which John Sells CounterfeitGoods To Jane}


It is crumbling and disintegrating, with a unwholesome black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with highly colourful stalls, with smoggy smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from maple and covered with cobalt double gauze.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pipe made by Disney.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 472 Imperial Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Makes Threats Against Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Taurus Model 608.
John waves at Jane with his revolver. Her face whitens, and John knows that she will yield to with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Engages In Reconnaisance About Jane}


He's using a ebony pair of binoculars, made in Disneyworld.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her study window.
John knows Jane's secret. What is her secret? She is a idemromantic agenderfluid gigabear, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a convoluted network of ropes, made from steel.
John throttles Jane.
Her face turns sky{-}blue.
\subsection{A Timeline In Which Jane Is A Escort, And John Is Her Customer}


The brothel has a crimson carpet floor, and the walls are painted crimson.
Jane's personal serving{-}room has a titanium bed, with orange tulip petals strewn about it.
Jane is dressed in a red bikini made from muslin.
John pays Jane 342 Imperial Guilders.
John crawls into her green tent.
Jane screams in impious delight, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a bootless fool{-}born schmuck?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was unerring, Jane thinks.
In fact, the more she assesses his argument, the more she realizes it was almost certainly correct, and resigns herself.
Jane pulls out a revolver {-} a OTs{-}20 Gnom {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Bubblegum gobs spatter across the cobalt walls, and carmine ichor pools upon the floor.
\subsection{A Timeline In Which John Distresses Jane}


John immobilizes Jane, using a specially modified bed, made from osmium.
He then gags her, using a rubber ring{-}gag.
John turns on the device, and the yellow suction caps work their magic upon her.
Jane howls through her gag, writhing about.
\subsection{A Timeline In Which John Stalks Jane}


He's using a plastic laser microphone, made in Russia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her attic window.
John knows Jane's secret. What is her secret? She is a amicussexual geminigender centitiger, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Milks Jane}


John pulls out a letter, encased in a orange envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} redskunk404@ymail.green {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a azure envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} pinkrat450@smail.landica {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Cajoles Jane}


The apartment has a cream stone floor, and the walls are painted orange.
The bedroom has a oak bed, with orange daffodil petals strewn about it.
John darts over to Jane, and licks her lips.
John sniffs her rose toothpaste.
Jane bellows in fiendish euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Sells ForgedGoods To Jane}


It is dreary and dilapidated, with a seedy black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}coloured stalls, with opaque smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from pine and covered with crimson linen.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit handbag made by Montblanc.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 169 Marvelous Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Cajoles Jane}


The apartment has a green stone floor, and the walls are painted cyan.
The bedroom has a osmium bed, with salmon daffodil petals strewn about it.
John saunters to Jane, and lightly bites her neck.
John smothers her peach furniture.
Jane screams in base relish, and John continues throughout the night...
\subsection{A Timeline In Which John Pierces Jane With A Blade}


John immobilizes Jane, using a wire frame, made from plastic.
John pulls out a cream spear, made out of ceramic.
He transfixes Jane with the spear.
Sanguine liquid rushes out from the wound.
\subsection{A Timeline In Which John Stains Jane}


John breaks into the apartment with a lead sledgehammer, and looks around.
The apartment has a teal stone floor, and the walls are painted red.
John prowls into Jane's bedroom.
John immobilizes Jane, using a virtual reality device, made from steel.
He then gags her, using a rubber ball{-}gag.
John crawls into her rose Disney merchandise.
Jane cries out in sacrilegious euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a set of straps, made from cotton.
John throttles Jane.
Her face turns magenta.
\subsection{A Timeline In Which John Sells PiratedGoods To Jane}


It is dilapidated and sombre, with a nasty black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with psychedelic stalls, with dense haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from spruce and covered with scarlet silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pen made by Versace.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 222 Bear Crowns, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a weedy onion{-}eyed flax{-}wench?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was correct, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly spot on, and resigns herself.
Jane pulls out a revolver {-} a Manurhin MR 73 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Salmon lumps slosh across the cyan walls, and scarlet fluid pools upon the floor.
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Digwasp is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Digwasp is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a idemromantic mirrorgender centifox, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is gloomy and dilapidated, with a nasty black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with polychromatic stalls, with thick smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from rosewood and covered with emerald cotton.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pair of earrings made by Versace.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 357 Bear Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Befouls Jane}


John breaks into the apartment with a glass hammer, and looks around.
The apartment has a purple carpet floor, and the walls are painted emerald.
John steals into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from ivory.
He then gags her, using a glass ring{-}gag.
John locks her lilac system.
Jane shouts in diabolical excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Steals From Jane}


Jane was striding past a dark alley.
It is dark and derelict, with a sordid black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see yellow walls inside the building.
John steps out of the gloom, catching Jane off{-}guard.
He pokes her with an illegally bought revolver, a Taurus Model 608.
He orders Jane to give him his money.
Trembling with fear, she hands him her pocketbook.
She takes her change and runs for it, thankful that she survived.
John receives 147 Bull Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Spikes A Drink For Jane}


John pulls out a small purple packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than butallol, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Mojito.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly nauseous, but it passes.
More dangerously, however, she is rendered malleable, which is exactly as John wants her...
\subsection{A Timeline In Which John Watches Jane}


He's using a glass satellite dish, made in Prussia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her conservatory window.
John knows Jane's secret. What is her secret? She is a desinoromantic duragender septosnail, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a salmon cement floor, and the walls are painted pink.
Jane's personal serving{-}room has a spruce bed, with azure chrysantheum petals strewn about it.
Jane is dressed in a cream teddy made from muslin.
John pays Jane 138 Ivory Nickels.
John pushs her orange bomb site B.
Jane bellows in degenerate indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a ivory spyglass, made in Czechoslovakia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her box room window.
John knows Jane's secret. What is her secret? She is a aroflux boggender millikangaroo, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Charms Jane}


The apartment has a azure cement floor, and the walls are painted cream.
The bedroom has a ebony bed, with blonde iris petals strewn about it.
John drifts to Jane, and sucks upon her cheek.
John spreads her blonde system.
Jane cries out in depraved indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Bilks Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: James Bankole[greencoyote294@bmail.net]
\\
I am Doctor James Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 18th of February, 1914, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 712 tonnes of ebony Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 18\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor James Bankole
\\\\
Jane thinks that this guy is really honest, and sends him some money.
John receives 365 Adamantine Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a teal concrete floor, and the walls are painted yellow.
Jane's personal serving{-}room has a osmium bed, with salmon rose petals strewn about it.
Jane is dressed in a rose babydoll made from satin.
John pays Jane 453 Planetary Hawks.
John grinds her aquamarine Disney merchandise.
Jane howls in profane sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a weedy fool{-}born fool?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was on the right track, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly on the nail, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 500 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Strawberry lumps moisten the orange walls, and cerise blood pools upon the floor.
\subsection{A Timeline In Which John Vitiates Jane}


John breaks into the apartment with a lead lockpick, and looks around.
The apartment has a yellow tile floor, and the walls are painted cobalt.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from steel.
He then gags her, using a hemp ball{-}gag.
John soaks her cyan spork.
Jane squeals in sacrilegious bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Robs Jane}


Jane was strolling past a dark alley.
It is dim and dim, with a corrupt opium den hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see cyan walls inside the building.
John steps out of the shade, taking Jane by surprise.
He pokes her with an illegally bought revolver, a Chiappa Rhino.
He instructs Jane to give him his money.
Shuddering with fear, she hands him her pochette.
She takes her change and runs for it, thankful that she survived.
John receives 388 Elevated Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Distresses Jane}


John immobilizes Jane, using a set of straps, made from cotton.
He then gags her, using a aluminium spider{-}gag.
John turns on the device, and the teal suction caps work their magic upon her.
Jane whimpers through her gag, squirming.
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a specially modified bed, made from iridium.
John asphyxiates Jane.
Her face turns lavender.
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a wire frame, made from titanium.
He then gags her, using a steel ball{-}gag.
John turns on the device, and the scarlet suction caps work their magic upon her.
Jane whines through her gag, writhing about.
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small orange packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than tryptocycline, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Mai Tai.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly dizzy, but it passes.
More dangerously, however, she is rendered flexible, which is exactly as John wants her...
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Airmap is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airmap is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a heteroflexible aliusgender megaeagle, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Intimidates Jane With A Revolver}


John is sitting in the bookstore.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Chiappa Rhino.
John gestures at Jane with his revolver. Her face blanches, and John knows that she will capitulate to with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Cyberwolf is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Cyberwolf is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a nocismasexual vagueflux centirabbit, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a wire frame, made from cotton.
He then gags her, using a titanium spider{-}gag.
John turns on the device, and the teal electrodes work their magic upon her.
Jane screams through her gag, trying to escape.
\subsection{A Timeline In Which John Tantalizes Jane}


The apartment has a azure linoleum floor, and the walls are painted apricot.
The bedroom has a glass bed, with green daffodil petals strewn about it.
John strolls to Jane, and kisses her cheek.
John rubs her peach Disney merchandise.
Jane cries out in blasphemous ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a brainwasher, made from leather.
John strangles Jane.
Her face turns turquoise.
\subsection{A Timeline In Which John Steals From Jane}


Jane was walking past a dark alley.
It is dreary and ruinous, with a unwholesome bordello hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see cream walls inside the building.
John steps out of the shadows, surprising Jane.
He prods her with an illegally bought revolver, a Chiappa Rhino.
He orders Jane to give him his money.
Shaking with fear, she hands him her pocketbook.
She takes her change and legs it, thankful that she survived.
John receives 403 Adamantine Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Cheats Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: URGENT
FROM: Jamie Bonganti[bluetiger234@mmail.int]
\\
I am Doctor Jamie Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 13th of May, 1987, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 666 tonnes of osmium Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 36\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Jamie Bonganti
\\\\
Jane thinks that this guy is really full of integrity, and sends him some money.
John receives 442 Planetary Bits, and is pleased with his gain.
\subsection{A Timeline In Which John Violates Jane}


John breaks into the apartment with a titanium sledgehammer, and looks around.
The apartment has a emerald tile floor, and the walls are painted red.
John steals into Jane's bedroom.
John immobilizes Jane, using a frame, made from osmium.
He then gags her, using a uranium glass rag.
John grinds her blonde spoon.
Jane screams in degenerate indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Agonizes Jane}


John immobilizes Jane, using a brainwasher, made from hemp.
He then gags her, using a hemp ring{-}gag.
John turns on the device, and the purple spikes work their magic upon her.
Jane shrieks through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Pressurizes Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Taurus Model 608.
John gestures at Jane with his revolver. Her face whitens, and John knows that she will go along with with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Distresses Jane}


John immobilizes Jane, using a forcefield generator, made from aluminium.
He then gags her, using a ebony ring{-}gag.
John turns on the device, and the cobalt constricting straps work their magic upon her.
Jane screams through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Pierces Jane With A Blade}


John immobilizes Jane, using a specially modified bed, made from titanium.
John pulls out a rose tactical knife, made out of Damascus stel.
He gashes Jane with the tactical knife.
Claret liquid cascades out from the wound.
\subsection{A Timeline In Which John Watches Jane}


He's using a plastic pair of binoculars, made in Palestine.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her kitchen window.
John knows Jane's secret. What is her secret? She is a apachehelisexual amogender kilodragon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Violates Jane}


John breaks into the apartment with a uranium glass crowbar, and looks around.
The apartment has a emerald wood floor, and the walls are painted cobalt.
John sneaks into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from rubber.
He then gags her, using a leather rag.
John crawls into her orange system.
Jane shouts in impious bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Narcotizes Jane}


John pulls out a small pink packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than esomeglitazone, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Cosmopolitan.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels nauseous, but it passes.
More dangerously, however, she is rendered docile, which is exactly as John wants her...
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a azure stone floor, and the walls are painted apricot.
Jane's personal serving{-}room has a aluminium bed, with teal tulip petals strewn about it.
Jane is dressed in a mint dress made from silk.
John pays Jane 486 Emerald Bills.
John unlocks her mauve goat.
Jane shouts in diabolical bliss, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a lilac cement floor, and the walls are painted crimson.
Jane's personal serving{-}room has a uranium glass bed, with orange tulip petals strewn about it.
Jane is dressed in a teal babydoll made from flax.
John pays Jane 301 Marvelous Quarters.
John brushes her scarlet rabbit.
Jane squeals in sacrilegious gratification, and John continues throughout the night...
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small pink packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than linazepam, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Gimlet.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very dizzy, but it passes.
More dangerously, however, she is rendered susceptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a wire frame, made from titanium.
John strangulates Jane.
Her face turns cyan.
\subsection{A Timeline In Which John Violates Jane}


John breaks into the apartment with a plastic hammer, and looks around.
The apartment has a lilac wood floor, and the walls are painted azure.
John slips into Jane's bedroom.
John immobilizes Jane, using a forcefield generator, made from hemp.
He then gags her, using a glass ball{-}gag.
John wraps her salmon bomb site B.
Jane howls in fiendish relish, and John continues throughout the night...
\subsection{A Timeline In Which John Harrows Jane}


John immobilizes Jane, using a virtual reality device, made from ebony.
He then gags her, using a plastic rag.
John turns on the device, and the red blades work their magic upon her.
Jane shrieks through her gag, writhing about.
\subsection{A Timeline In Which John Demands Hush Money From Jane}


John pulls out a letter, encased in a mauve envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} purpleotter102@ymail.wine {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a frothy crook{-}pated fool?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was on the mark, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly on the nail, and resigns herself.
Jane pulls out a revolver {-} a Taurus Model 608 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink chunks soak the yellow walls, and flaming ichor pools upon the floor.
\subsection{A Timeline In Which John Steals From Jane}


Jane was strolling past a dark alley.
It is grim and ruinous, with a disreputable opium den hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see apricot walls inside the building.
John steps out of the shadows, taking Jane by surprise.
He nudges her with an illegally bought revolver, a Taurus Model 608.
He instructs Jane to give him his money.
Shaking with fear, she hands him her purse.
She takes her change and runs for it, thankful that she survived.
John receives 466 Perfected Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Threatens Jane With A Revolver}


John is sitting in the bar.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Smith \& Wesson Model 500.
John gesticulates at Jane with his revolver. Her face pales, and John knows that she will relent to with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which Jane Is A 'Companion', And John Is Her Customer}


The brothel has a blue concrete floor, and the walls are painted green.
Jane's personal serving{-}room has a spruce bed, with cyan tulip petals strewn about it.
Jane is dressed in a pink babydoll made from gauze.
John pays Jane 324 Golden Pieces.
John crawls into her teal spoon.
Jane cries out in profane joy, and John continues throughout the night...
\subsection{A Timeline In Which John Browbeats Jane With A Revolver}


John is sitting in the bar.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Taurus Judge.
John gesticulates at Jane with his revolver. Her face blanches, and John knows that she will go along with with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a frame, made from ebony.
John pulls out a mauve trench{-}knife, made out of Damascus stel.
He slashes Jane with the trench{-}knife.
Ruby ichor floods out from the wound.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a frothy doghearted pigeon{-}egg?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was on the mark, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly unerring, and resigns herself.
Jane pulls out a revolver {-} a Manurhin MR 73 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink gobs drench the cobalt walls, and cerise fluid pools upon the floor.
\subsection{A Timeline In Which John Engages In Reconnaisance About Jane}


He's using a plastic long{-}range camera, made in Israel.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her kitchen window.
John knows Jane's secret. What is her secret? She is a culparomantic aethergender heptomouse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a forcefield generator, made from glass.
John garrottes Jane.
Her face turns lavender.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is gloomy and dreary, with a sleazy cult hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see blue walls inside the building.
John steps out of the darkness, catching Jane off{-}guard.
He jabs her with an illegally bought revolver, a MP{-}412 REX.
He orders Jane to give him his money.
Trembling with fear, she hands him her pocketbook.
She takes her change and scarpers off, thankful that she survived.
John receives 270 Marvelous Crowns, and is pleased with his gain.
\subsection{A Timeline In Which John Sells ImitationGoods To Jane}


It is broken{-}down and gloomy, with a corrupt black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with kaleidoscopic stalls, with dense smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from maple and covered with cream double gauze.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pipe made by Gucci.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 327 Prismatic Crowns, and is pleased with his gain.
\subsection{A Timeline In Which John Alarms Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Smith \& Wesson Model 500.
John waves at Jane with his revolver. Her face loses colour, and John knows that she will go along with with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Wirespider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Wirespider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a idemromantic dryagender gigaskunk, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Pollutes Jane}


John breaks into the apartment with a glass hacking PDA, and looks around.
The apartment has a azure vinyl floor, and the walls are painted peach.
John sneaks into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from glass.
He then gags her, using a rubber ball{-}gag.
John unlocks her mint furniture.
Jane howls in diabolical relish, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a bootless sheep{-}biting fool?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was veracious, Jane thinks.
In fact, the more she reviews his argument, the more she realizes it was almost certainly precise, and resigns herself.
Jane pulls out a revolver {-} a Charter Arms Bulldog {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rosy lumps spatter across the crimson walls, and cherry ichor pools upon the floor.
\subsection{A Timeline In Which John Pierces Jane With A Blade}


John immobilizes Jane, using a frame, made from plastic.
John pulls out a apricot knife, made out of iron.
He stabs Jane with the knife.
Flaming blood rushes out from the wound.
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a azure linoleum floor, and the walls are painted apricot.
Jane's personal serving{-}room has a mahogany bed, with yellow tulip petals strewn about it.
Jane is dressed in a blonde minidress made from lace.
John pays Jane 264 Bull Quarters.
John sniffs her peach llama.
Jane howls in depraved delight, and John continues throughout the night...
\subsection{A Timeline In Which John Violates Jane}


John breaks into the apartment with a uranium glass crowbar, and looks around.
The apartment has a cream stone floor, and the walls are painted lilac.
John steals into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from uranium glass.
He then gags her, using a iridium spider{-}gag.
John drills her scarlet furniture.
Jane screams in unspeakable sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Call Girl, And John Is Her Customer}


The brothel has a pink linoleum floor, and the walls are painted rose.
Jane's personal serving{-}room has a marble bed, with red tulip petals strewn about it.
Jane is dressed in a peach teddy made from lace.
John pays Jane 170 Emerald Dollars.
John locks her purple spork.
Jane bellows in dark joy, and John continues throughout the night...
\subsection{A Timeline In Which John Debauches Jane}


John breaks into the apartment with a iridium hacking PDA, and looks around.
The apartment has a yellow carpet floor, and the walls are painted rose.
John prowls into Jane's bedroom.
John immobilizes Jane, using a forcefield generator, made from ivory.
He then gags her, using a cotton ring{-}gag.
John milks her orange goat.
Jane shouts in sacrilegious indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Tempts Jane}


The apartment has a peach carpet floor, and the walls are painted blue.
The bedroom has a uranium glass bed, with blue hyacinth petals strewn about it.
John walks to Jane, and sucks upon her lips.
John smothers her purple boat.
Jane cries out in unspeakable gratification, and John continues throughout the night...
\subsection{A Timeline In Which John Punctures Jane With A Blade}


John immobilizes Jane, using a brainwasher, made from rubber.
John pulls out a mint sword, made out of titanium.
He wounds Jane with the sword.
Red liquid spouts out from the wound.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a ivory long{-}range camera, made in England.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her greenhouse window.
John knows Jane's secret. What is her secret? She is a aliquasexual proxvir quintofox, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Laces A Drink For Jane}


John pulls out a small salmon packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than doxyfil, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Gimlet.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly dizzy, but it passes.
More dangerously, however, she is rendered malleable, which is exactly as John wants her...
\subsection{A Timeline In Which John Allures Jane}


The apartment has a purple concrete floor, and the walls are painted aquamarine.
The bedroom has a iridium bed, with peach tulip petals strewn about it.
John wanders to Jane, and licks her cheek.
John parks in her green chicken.
Jane bellows in profane excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Frightens Jane With A Revolver}


John is sitting in the cafe.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Chiappa Rhino.
John waves at Jane with his revolver. Her face becomes pale, and John knows that she will go along with with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Sells PhonyGoods To Jane}


It is dismal and ruinous, with a sordid black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with varicoloured stalls, with soupy haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from hickory and covered with rose rayon.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit smartphone made by Rolex.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 133 Marvelous Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a convoluted network of ropes, made from cotton.
John strangulates Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a aquamarine envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} pinkskunk975@hmail.audio {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a yellow envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} aquamarinehyena414@xmail.build {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Befouls Jane}


John breaks into the apartment with a steel crowbar, and looks around.
The apartment has a cobalt concrete floor, and the walls are painted crimson.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from steel.
He then gags her, using a cotton ring{-}gag.
John brushes her rose furniture.
Jane howls in unspeakable sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a specially modified bed, made from ebony.
John throttles Jane.
Her face turns azure.
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a emerald envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} redcheetah46@omail.sucks {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is dilapidated and disintegrating, with a unpleasant black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with like a rainbow stalls, with murky smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from beech and covered with pink flannel.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit knife made by Chanel.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 314 Prismatic Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a droning earth{-}vexing flax{-}wench?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was precise, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly precise, and resigns herself.
Jane pulls out a revolver {-} a Charter Arms Bulldog {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Salmon gobs soak the salmon walls, and sanguine blood pools upon the floor.
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a frame, made from titanium.
John strangulates Jane.
Her face turns azure.
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small yellow packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than esometyline, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly dizzy, but it passes.
More dangerously, however, she is rendered adaptable, which is exactly as John wants her...
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a frame, made from glass.
John pulls out a mint sword, made out of ceramic.
He gashes Jane with the sword.
Carmine liquid rushes out from the wound.
\subsection{A Timeline In Which John Sells PiratedGoods To Jane}


It is cheerless and drab, with a corrupt black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with multicolour stalls, with smoggy smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from rosewood and covered with orange cotton.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit knife made by Versace.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 500 Bull Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Digphoenix is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Digphoenix is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a arospike seagender terahyena, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a hypnosis machine, made from cotton.
John pulls out a scarlet sword, made out of newspaper.
He perforates Jane with the sword.
Cherry blood pours out from the wound.
\subsection{A Timeline In Which John Defiles Jane}


John breaks into the apartment with a tungsten lockpick, and looks around.
The apartment has a pink vinyl floor, and the walls are painted apricot.
John prowls into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from cotton.
He then gags her, using a ivory ring{-}gag.
John soaks her aquamarine llama.
Jane bellows in fiendish joy, and John continues throughout the night...
\subsection{A Timeline In Which John Scams Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Mike Okon[azureferret659@qmail.orange]
\\
I am Minister Mike Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 30th of September, 1949, my client and his wife and their only daughter were involved in bomb blast here in my country.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 528 tonnes of osmium Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 49\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Mike Okon
\\\\
Jane thinks that this guy is really trustworthy, and sends him some money.
John receives 209 Marvelous Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Alarms Jane With A Revolver}


John is sitting in the library.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Charter Arms Bulldog.
John gesticulates at Jane with his revolver. Her face turns pallid, and John knows that she will relent to with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Laces A Drink For Jane}


John pulls out a small blue packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than sulfacemycin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Gimlet.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly nauseous, but it passes.
More dangerously, however, she is rendered susceptible, which is exactly as John wants her...
\subsection{A Timeline In Which John Threatens To Harm Jane With A Revolver}


John is sitting in the park.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a U{-}94 Udar.
John waves at Jane with his revolver. Her face whitens, and John knows that she will go along with with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Fleeces Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Jamie Smith[blondeskunk721@xmail.scotchwhisky]
\\
I am Barrister Jamie Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 31th of August, 1932, my client and his wife and their only daughter were involved in bomb blast here in my country.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1579 tonnes of rubber Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 17\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Jamie Smith
\\\\
Jane thinks that this guy is really virtuous, and sends him some money.
John receives 325 Adamantine Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a brainwasher, made from rubber.
He then gags her, using a rubber spider{-}gag.
John turns on the device, and the blue electrodes work their magic upon her.
Jane moans through her gag, thrashing about.
\subsection{A Timeline In Which Jane Is A Escort, And John Is Her Customer}


The brothel has a mint stone floor, and the walls are painted cobalt.
Jane's personal serving{-}room has a steel bed, with crimson chrysantheum petals strewn about it.
Jane is dressed in a aquamarine nightgown made from cotton.
John pays Jane 291 Marvelous Dollars.
John drills her scarlet furniture.
Jane squeals in dark excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Sells ErsatzGoods To Jane}


It is grim and broken{-}down, with a rough black market hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with psychedelic stalls, with opaque smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from birch and covered with apricot satin.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit watch made by Versace.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 177 Ivory Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Pressures Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Smith \& Wesson Model 340PD.
John gesticulates at Jane with his revolver. Her face becomes pale, and John knows that she will yield to with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Fleeces Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: URGENT
FROM: Ken Bankole[orangekangaroo821@kmail.academy]
\\
I am Doctor Ken Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 7th of November, 1945, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 169 tonnes of hemp Left behind by my client before it get confiscated or declared unservicable by Plunder \& Flee Incorporated, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Plunder \& Flee Incorporated have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 41\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Ken Bankole
\\\\
Jane thinks that this guy is really incorruptible, and sends him some money.
John receives 453 Bear Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Mugs Jane}


Jane was strolling past a dark alley.
It is crumbling and run{-}down, with a rough speakeasy hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see cyan walls inside the building.
John steps out of the gloom, taking Jane by surprise.
He nudges her with an illegally bought revolver, a Chiappa Rhino.
He directs Jane to give him his money.
Quivering with fear, she hands him her billfold.
She takes her change and escapes, thankful that she survived.
John receives 159 Golden Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Torments Jane}


John immobilizes Jane, using a wire frame, made from aluminium.
He then gags her, using a glass ring{-}gag.
John turns on the device, and the purple spikes work their magic upon her.
Jane shrieks through her gag, squirming.
\subsection{A Timeline In Which John Pressurizes Jane With A Revolver}


John is sitting in the pub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Colt Anaconda.
John gestures at Jane with his revolver. Her face loses colour, and John knows that she will yield to with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Studies Jane Using The Internet}


Metaspider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Metaspider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a objectumsexual mosaigender teradog, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which Jane Is A Lady Of The Night, And John Is Her Customer}


The brothel has a peach carpet floor, and the walls are painted mauve.
Jane's personal serving{-}room has a spruce bed, with cobalt hyacinth petals strewn about it.
Jane is dressed in a peach teddy made from lace.
John pays Jane 393 Elevated Ducats.
John grinds her aquamarine rabbit.
Jane squeals in fiendish sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a convoluted network of ropes, made from titanium.
John throttles Jane.
Her face turns azure.
\subsection{A Timeline In Which John Torments Jane}


John immobilizes Jane, using a frame, made from glass.
He then gags her, using a plastic ball{-}gag.
John turns on the device, and the pink electrodes work their magic upon her.
Jane moans through her gag, squirming.
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a peevish hell{-}hated clack{-}dish?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was on the right track, Jane thinks.
In fact, the more she assesses his argument, the more she realizes it was almost certainly spot on, and resigns herself.
Jane pulls out a revolver {-} a U{-}94 Udar {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Bubblegum masses soak the pink walls, and flaming ichor pools upon the floor.
\subsection{A Timeline In Which John Agonizes Jane}


John immobilizes Jane, using a set of straps, made from uranium glass.
He then gags her, using a glass rag.
John turns on the device, and the yellow constricting straps work their magic upon her.
Jane whines through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Violates Jane}


John breaks into the apartment with a steel hammer, and looks around.
The apartment has a aquamarine wood floor, and the walls are painted purple.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a frame, made from hemp.
He then gags her, using a osmium rag.
John parks in her blue tent.
Jane screams in wicked excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a set of straps, made from steel.
He then gags her, using a iridium spider{-}gag.
John turns on the device, and the emerald blades work their magic upon her.
Jane screams through her gag, squirming.
\subsection{A Timeline In Which John Befouls Jane}


John breaks into the apartment with a osmium crowbar, and looks around.
The apartment has a apricot stone floor, and the walls are painted crimson.
John slips into Jane's bedroom.
John immobilizes Jane, using a forcefield generator, made from cotton.
He then gags her, using a hemp ring{-}gag.
John grinds her cobalt chicken.
Jane cries out in blasphemous relish, and John continues throughout the night...
\subsection{A Timeline In Which John Extorts Money From Jane}


John pulls out a letter, encased in a cream envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} peachcheetah34@vmail.audio {-} he added soon...
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Swindles Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Jamie Smith[emeraldskunk801@zmail.cyan]
\\
I am Minister Jamie Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 9th of April, 1924, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 10983 tonnes of osmium Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 28\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Smith
\\\\
Jane thinks that this guy is really above suspicion, and sends him some money.
John receives 334 Emerald Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a osmium spyglass, made in Uzbekistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her conservatory window.
John knows Jane's secret. What is her secret? She is a antihaemosexual stargender decaleopard, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Fleeces Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Ken Okon[lilacwolf136@zmail.yellow]
\\
I am Minister Ken Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 3th of October, 1971, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 528 tonnes of plastic Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 24\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Ken Okon
\\\\
Jane thinks that this guy is really above suspicion, and sends him some money.
John receives 452 Radiant Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a cyan envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} emeralddeer545@pmail.post {-} he added soon...
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Swindles Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: important and confidential
FROM: Jamie Okon[salmonsquirrel601@hmail.landica]
\\
I am Barrister Jamie Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 14th of March, 1914, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1598 tonnes of iridium Left behind by my client before it get confiscated or declared unservicable by Plunder \& Flee Incorporated, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Plunder \& Flee Incorporated have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 29\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Jamie Okon
\\\\
Jane thinks that this guy is really virtuous, and sends him some money.
John receives 186 Imperial Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is gloomy and dark, with a unwholesome black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with highly colourful stalls, with thick smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from ash and covered with emerald double gauze.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit fountain pen made by Rolex.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 290 Planetary Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Debases Jane}


John breaks into the apartment with a glass sledgehammer, and looks around.
The apartment has a cobalt cement floor, and the walls are painted red.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a virtual reality device, made from aluminium.
He then gags her, using a iridium ring{-}gag.
John sniffs her blonde boat.
Jane cries out in unspeakable euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Mesmerizes Jane}


The apartment has a crimson tile floor, and the walls are painted orange.
The bedroom has a hemp bed, with teal chrysantheum petals strewn about it.
John drifts to Jane, and sucks upon her lips.
John grinds her lilac seamstress.
Jane howls in degenerate delight, and John continues throughout the night...
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Cyberspider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Cyberspider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a amicussexual stargender centicoyote, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Metamap is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Metamap is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a culparomantic adeptogender hexasquirrel, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Threatens To Harm Jane With A Revolver}


John is sitting in the park.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Ruger Vaquero.
John motions at Jane with his revolver. Her face blanches, and John knows that she will capitulate to with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Milks Jane}


John pulls out a letter, encased in a blue envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} mauvelion845@cmail.pizza {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Menaces Jane With A Revolver}


John is sitting in the bookstore.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Charter Arms Bulldog.
John gestures at Jane with his revolver. Her face blanches, and John knows that she will give in to with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Airshark is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airshark is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a nocismasexual cloudgender triraccoon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Netphoenix is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Netphoenix is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a nocismasexual aesthetgender septoraccoon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Charms Jane}


The apartment has a aquamarine wood floor, and the walls are painted apricot.
The bedroom has a spruce bed, with apricot tulip petals strewn about it.
John strolls to Jane, and lightly bites her cheek.
John unlocks her crimson boat.
Jane cries out in depraved delight, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a blonde carpet floor, and the walls are painted mint.
Jane's personal serving{-}room has a hemp bed, with orange iris petals strewn about it.
Jane is dressed in a mint nightgown made from flax.
John pays Jane 215 Indigo Bills.
John grinds her peach swamp.
Jane howls in sacrilegious joy, and John continues throughout the night...
\subsection{A Timeline In Which John Bullies Jane With A Revolver}


John is sitting in the library.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a U{-}94 Udar.
John gesticulates at Jane with his revolver. Her face loses colour, and John knows that she will yield to with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Maltreats Jane}


John immobilizes Jane, using a forcefield generator, made from glass.
He then gags her, using a titanium rag.
John turns on the device, and the apricot suction caps work their magic upon her.
Jane moans through her gag, trying to escape.
\subsection{A Timeline In Which John Steals From Jane}


Jane was strolling past a dark alley.
It is dull and broken{-}down, with a rough speakeasy hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see emerald walls inside the building.
John steps out of the shade, catching Jane off{-}guard.
He jabs her with an illegally bought revolver, a Charter Arms Bulldog.
He instructs Jane to give him his money.
Trembling with fear, she hands him her pocketbook.
She takes her change and runs for it, thankful that she survived.
John receives 453 Marvelous Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Pierces Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from hemp.
John pulls out a mauve dirk, made out of ceramic.
He gashes Jane with the dirk.
Gules fluid flows out from the wound.
\subsection{A Timeline In Which John Sells ImitationGoods To Jane}


It is decaying and shabby, with a disreputable black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with highly colourful stalls, with dense smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from redwood and covered with blonde linen.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit handbag made by Chanel.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 208 Imperial Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Engages In Reconnaisance About Jane}


He's using a glass long{-}range camera, made in Austria.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her study window.
John knows Jane's secret. What is her secret? She is a skoliosexual firegender heptoleopard, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good morning' to her.
He then insults her {-} 'By God, aren't you a froward sheep{-}biting jolt{-}head?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was on the money, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly correct, and resigns herself.
Jane pulls out a revolver {-} a OTs{-}20 Gnom {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rouge gobs moisten the mint walls, and sanguine fluid pools upon the floor.
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small salmon packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than acetamycin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly dizzy, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Charms Jane}


The apartment has a mint vinyl floor, and the walls are painted peach.
The bedroom has a osmium bed, with apricot rose petals strewn about it.
John walks to Jane, and massages her cheek.
John drills her apricot spoon.
Jane cries out in blasphemous ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Adulterates Jane}


John breaks into the apartment with a steel lockpick, and looks around.
The apartment has a mauve vinyl floor, and the walls are painted red.
John steals into Jane's bedroom.
John immobilizes Jane, using a forcefield generator, made from glass.
He then gags her, using a rubber spider{-}gag.
John milks her lilac bomb site B.
Jane cries out in degenerate excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a weedy fool{-}born mammet?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was flawless, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly unerring, and resigns herself.
Jane pulls out a revolver {-} a Colt Anaconda {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Taffy chunks spray the orange walls, and ruby ichor pools upon the floor.
\subsection{A Timeline In Which John Frightens Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Taurus Model 608.
John gesticulates at Jane with his revolver. Her face turns pallid, and John knows that she will give in to with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a brainwasher, made from iridium.
John strangles Jane.
Her face turns purple.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good evening' to her.
He then insults her {-} 'By God, aren't you a droning onion{-}eyed devil{-}monk?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was faultless, Jane thinks.
In fact, the more she ruminates over his argument, the more she realizes it was almost certainly unerring, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 340PD {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Coral lumps spatter the red walls, and gules liquid pools upon the floor.
\subsection{A Timeline In Which John Extorts Money From Jane}


John pulls out a letter, encased in a green envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} creameagle670@smail.adult {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Has His Way With Jane}


John breaks into the apartment with a uranium glass lockpick, and looks around.
The apartment has a apricot stone floor, and the walls are painted red.
John creeps into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from steel.
He then gags her, using a glass ring{-}gag.
John brushes her green goat.
Jane screams in degenerate pleasure, and John continues throughout the night...
\subsection{A Timeline In Which John Engages In Reconnaisance About Jane}


He's using a ebony pair of binoculars, made in Disneyworld.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her bathroom window.
John knows Jane's secret. What is her secret? She is a desinoromantic vectorgender heptobull, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Engages In Espionage Upon Jane}


He's using a iridium satellite dish, made in Australia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her attic window.
John knows Jane's secret. What is her secret? She is a iculasexual chaosflux gigakangaroo, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Engages In Reconnaisance About Jane}


He's using a glass satellite dish, made in Skxc8aistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her greenhouse window.
John knows Jane's secret. What is her secret? She is a kalossexual proxvir millihyena, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is cheerless and broken{-}down, with a disreputable black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with dense smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from oak and covered with rose linen.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigarettes made by Versace.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 162 Bull Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Bilks Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Ken Okon[emeraldhorse48@pmail.scotchwhisky]
\\
I am Minister Ken Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 23th of April, 1996, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1598 tonnes of uranium glass Left behind by my client before it get confiscated or declared unservicable by Plunder \& Flee Incorporated, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Plunder \& Flee Incorporated have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 33\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Ken Okon
\\\\
Jane thinks that this guy is really ethical, and sends him some money.
John receives 492 Radiant Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Sells ErsatzGoods To Jane}


It is drab and dull, with a unpleasant black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with technicolour stalls, with soupy smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from mahogany and covered with azure double gauze.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigarettes made by Versace.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 354 Radiant Notes, and is pleased with his gain.
\subsection{A Timeline In Which John Sells CounterfeitGoods To Jane}


It is dark and grimy, with a unwholesome black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with kaleidoscopic stalls, with soupy smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from pine and covered with mint cotton.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit knife made by Montblanc.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 392 Perfected Crowns, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a azure vinyl floor, and the walls are painted cyan.
Jane's personal serving{-}room has a aluminium bed, with azure iris petals strewn about it.
Jane is dressed in a azure negligee made from flax.
John pays Jane 460 Adamantine Dollars.
John sniffs her cobalt llama.
Jane bellows in profane excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Watches Jane}


He's using a iridium telescope, made in Germany.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her hall window.
John knows Jane's secret. What is her secret? She is a akiosexual genderblur hexaleopard, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Rips Off Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Mike Bonganti[orangehorse27@ymail.io]
\\
I am Barrister Mike Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 27th of August, 1967, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1579 tonnes of cotton Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 35\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Mike Bonganti
\\\\
Jane thinks that this guy is really virtuous, and sends him some money.
John receives 349 Planetary Quarters, and is pleased with his gain.
\subsection{A Timeline In Which John Sells CounterfeitGoods To Jane}


It is dismal and grimy, with a corrupt black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with kaleidoscopic stalls, with thick haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from hickory and covered with mauve denim.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pair of earrings made by Chanel.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 243 Radiant Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Charms Jane}


The apartment has a salmon cement floor, and the walls are painted scarlet.
The bedroom has a spruce bed, with lilac chrysantheum petals strewn about it.
John walks to Jane, and kisses her lips.
John tempts her lilac zoo.
Jane cries out in godless bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Demands Hush Money From Jane}


John pulls out a letter, encased in a green envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} cobaltsquirrel823@imail.post {-} he added soon...
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Intimidates Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a OTs{-}20 Gnom.
John gestures at Jane with his revolver. Her face blanches, and John knows that she will capitulate to with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a dankish idle{-}headed mammet?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was along the right lines, Jane thinks.
In fact, the more she contemplates his argument, the more she realizes it was almost certainly veracious, and resigns herself.
Jane pulls out a revolver {-} a Manurhin MR 73 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rosy masses soak the lilac walls, and claret ichor pools upon the floor.
\subsection{A Timeline In Which John Issues Threats To Jane With A Revolver}


John is sitting in the park.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a U{-}94 Udar.
John gesticulates at Jane with his revolver. Her face blanches, and John knows that she will go along with with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Keeps An Eye On Jane}


He's using a osmium telescope, made in Yugoslavia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her attic window.
John knows Jane's secret. What is her secret? She is a amicussexual amicagender hectohyena, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Milks Jane}


John pulls out a letter, encased in a pink envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} scarletrat791@mmail.social {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good evening' to her.
He then insults her {-} 'By God, aren't you a burly{-}boned rump{-}fed schmuck?
You know, Jane, maybe you should just end it all.'
Maybe his argument was right, Jane thinks.
In fact, the more she reviews his argument, the more she realizes it was almost certainly faultless, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 500 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Pale pink gobs bespatter the yellow walls, and rusty blood pools upon the floor.
\subsection{A Timeline In Which John Spoils Jane}


John breaks into the apartment with a ebony hacking PDA, and looks around.
The apartment has a emerald tile floor, and the walls are painted cobalt.
John slips into Jane's bedroom.
John immobilizes Jane, using a forcefield generator, made from plastic.
He then gags her, using a cotton ball{-}gag.
John soaks her scarlet zoo.
Jane shouts in fiendish bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Keeps An Eye On Jane}


He's using a steel long{-}range camera, made in Uzbekistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her ballroom window.
John knows Jane's secret. What is her secret? She is a platoniromantic invisigender uniwolf, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sells Knock{-}offGoods To Jane}


It is drab and dull, with a seamy black market hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with prismatic stalls, with soupy smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from oak and covered with yellow satin.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit handbag made by Versace.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 321 Indigo Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a wire frame, made from plastic.
He then gags her, using a hemp rag.
John turns on the device, and the red spikes work their magic upon her.
Jane screams through her gag, thrashing about.
\subsection{A Timeline In Which John Tortures Jane}


John immobilizes Jane, using a brainwasher, made from titanium.
He then gags her, using a ivory spider{-}gag.
John turns on the device, and the salmon suction caps work their magic upon her.
Jane moans through her gag, trying to escape.
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small azure packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than sitazepam, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Mojito.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a lewd hell{-}hated clack{-}dish?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was on the money, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly on the mark, and resigns herself.
Jane pulls out a revolver {-} a Colt Anaconda {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rouge bits spatter the lilac walls, and rusty liquid pools upon the floor.
\subsection{A Timeline In Which John Knocks Out Jane}


John pulls out a small green packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than saxaridone, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Nanhattan.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels fairly nauseous, but it passes.
More dangerously, however, she is rendered persuadable, which is exactly as John wants her...
\subsection{A Timeline In Which John Stabs Jane With A Blade}


John immobilizes Jane, using a forcefield generator, made from plastic.
John pulls out a crimson tactical knife, made out of newspaper.
He pierces Jane with the tactical knife.
Cherry fluid pours out from the wound.
\subsection{A Timeline In Which John Narcotizes Jane}


John pulls out a small salmon packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than avanatadine, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Mojito.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a vain crook{-}pated nut{-}hook?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was along the right lines, Jane thinks.
In fact, the more she evaluates his argument, the more she realizes it was almost certainly on the mark, and resigns herself.
Jane pulls out a revolver {-} a Chiappa Rhino {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink bits soak the mint walls, and sanguine fluid pools upon the floor.
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a virtual reality device, made from steel.
John pulls out a pink spear, made out of chrome.
He penetrates Jane with the spear.
Rosy blood spills out from the wound.
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Datahydra is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Datahydra is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a aromantic absorgender gigaeagle, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Defrauds Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Jamie Bonganti[mintsnail597@vmail.cyan]
\\
I am Doctor Jamie Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 12th of November, 1918, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 253 tonnes of cotton Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 15\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Jamie Bonganti
\\\\
Jane thinks that this guy is really ethical, and sends him some money.
John receives 382 Ivory Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Mugs Jane}


Jane was walking past a dark alley.
It is ruinous and grimy, with a disreputable cult hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see purple walls inside the building.
John steps out of the gloominess, surprising Jane.
He taps her with an illegally bought revolver, a Chiappa Rhino.
He directs Jane to give him his money.
Shaking with fear, she hands him her pochette.
She takes her change and slips away, thankful that she survived.
John receives 267 Radiant Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Bilks Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Jamie Bankole[lilacmouse335@rmail.probablyillegal]
\\
I am Barrister Jamie Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 29th of April, 1951, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 666 tonnes of uranium glass Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 35\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Jamie Bankole
\\\\
Jane thinks that this guy is really dependable, and sends him some money.
John receives 183 Marvelous Crowns, and is pleased with his gain.
\subsection{A Timeline In Which John Sells FakeGoods To Jane}


It is sombre and dull, with a unwholesome black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with polychromatic stalls, with soupy smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from beech and covered with yellow polyester.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit knife made by Prada.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 496 Radiant Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Harrows Jane}


John immobilizes Jane, using a specially modified bed, made from leather.
He then gags her, using a glass ball{-}gag.
John turns on the device, and the cobalt knives work their magic upon her.
Jane shrieks through her gag, writhing about.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a ebony long{-}range camera, made in China.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her cellar window.
John knows Jane's secret. What is her secret? She is a nocismasexual dryagender quintolion, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a peach tile floor, and the walls are painted lilac.
Jane's personal serving{-}room has a mahogany bed, with yellow daffodil petals strewn about it.
Jane is dressed in a teal minidress made from muslin.
John pays Jane 238 Ebony Notes.
John spreads her red swamp.
Jane bellows in base rapture, and John continues throughout the night...
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a virtual reality device, made from plastic.
John pulls out a apricot machete, made out of ivory.
He wounds Jane with the machete.
Ruby ichor gushes out from the wound.
\subsection{A Timeline In Which John Exploits Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Ken Okon[mauvehyena723@smail.yellow]
\\
I am Minister Ken Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 3th of April, 1979, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 253 tonnes of uranium glass Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 13\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Ken Okon
\\\\
Jane thinks that this guy is really trustworthy, and sends him some money.
John receives 479 Emerald Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a set of straps, made from titanium.
He then gags her, using a aluminium ball{-}gag.
John turns on the device, and the scarlet blades work their magic upon her.
Jane whines through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Spikes A Drink For Jane}


John pulls out a small emerald packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than futaprazole, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Gimlet.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly dizzy, but it passes.
More dangerously, however, she is rendered pliable, which is exactly as John wants her...
\subsection{A Timeline In Which John Spikes A Drink For Jane}


John pulls out a small teal packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than esomenacin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly dizzy, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which Jane Is A 'Companion', And John Is Her Customer}


The brothel has a crimson stone floor, and the walls are painted lilac.
Jane's personal serving{-}room has a leather bed, with blonde rose petals strewn about it.
Jane is dressed in a purple minidress made from cashmere.
John pays Jane 399 Marvelous Sultanates.
John locks her teal chicken.
Jane shouts in base delight, and John continues throughout the night...
\subsection{A Timeline In Which John Dupes Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Mike Okon[lilacrat790@wmail.red]
\\
I am Barrister Mike Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 14th of April, 1951, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 528 tonnes of osmium Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 26\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Mike Okon
\\\\
Jane thinks that this guy is really responsible, and sends him some money.
John receives 211 Ebony Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Knocks Out Jane}


John pulls out a small aquamarine packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than butalsone, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Martini.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered impressionable, which is exactly as John wants her...
\subsection{A Timeline In Which John Dupes Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Mike Bonganti[blueleopard499@chainmail.academy]
\\
I am Doctor Mike Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 14th of July, 1984, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1579 tonnes of plastic Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 41\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Mike Bonganti
\\\\
Jane thinks that this guy is really dependable, and sends him some money.
John receives 350 Ivory Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Frightens Jane With A Revolver}


John is sitting in the bar.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Manurhin MR 73.
John waves at Jane with his revolver. Her face blanches, and John knows that she will yield to with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Kills Jane With A Blade}


John immobilizes Jane, using a forcefield generator, made from leather.
John pulls out a pink sword, made out of steel.
He slashes Jane with the sword.
Sanguine liquid rushes out from the wound.
\subsection{A Timeline In Which Jane Is A 'Companion', And John Is Her Customer}


The brothel has a cream wood floor, and the walls are painted emerald.
Jane's personal serving{-}room has a iridium bed, with purple hyacinth petals strewn about it.
Jane is dressed in a peach nightgown made from cashmere.
John pays Jane 267 Perfected Quarters.
John rubs her apricot bomb site B.
Jane squeals in blasphemous ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a rose tile floor, and the walls are painted yellow.
Jane's personal serving{-}room has a cotton bed, with cobalt iris petals strewn about it.
Jane is dressed in a peach negligee made from silk.
John pays Jane 147 Prismatic Marks.
John grinds her blonde boat.
Jane squeals in dark ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Sells PiratedGoods To Jane}


It is decaying and sombre, with a unwholesome black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with polychromatic stalls, with murky smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from redwood and covered with purple silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigar made by Montblanc.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 283 Bear Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a hypnosis machine, made from ebony.
John strangulates Jane.
Her face turns magenta.
\subsection{A Timeline In Which John Milks Jane}


John pulls out a letter, encased in a crimson envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} orangeeagle749@zmail.red {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Distresses Jane}


John immobilizes Jane, using a specially modified bed, made from iridium.
He then gags her, using a plastic rag.
John turns on the device, and the orange suction caps work their magic upon her.
Jane wails through her gag, trying to escape.
\subsection{A Timeline In Which Jane Is A Lady Of The Night, And John Is Her Customer}


The brothel has a peach linoleum floor, and the walls are painted crimson.
Jane's personal serving{-}room has a cotton bed, with purple daffodil petals strewn about it.
Jane is dressed in a red minidress made from muslin.
John pays Jane 460 Emerald Hawks.
John flosses her aquamarine boat.
Jane cries out in wicked delight, and John continues throughout the night...
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a steel long{-}range camera, made in Austria{-}Hungary.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her living room window.
John knows Jane's secret. What is her secret? She is a intraromantic canisgender hectohyena, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Titillates Jane}


The apartment has a cream tile floor, and the walls are painted azure.
The bedroom has a ebony bed, with salmon tulip petals strewn about it.
John walks to Jane, and sucks upon her lips.
John wraps her blonde toothpaste.
Jane squeals in degenerate sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Harrows Jane}


John immobilizes Jane, using a wire frame, made from aluminium.
He then gags her, using a osmium ball{-}gag.
John turns on the device, and the cobalt blades work their magic upon her.
Jane shrieks through her gag, writhing about.
\subsection{A Timeline In Which John Sells ErsatzGoods To Jane}


It is grimy and dismal, with a corrupt black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with kaleidoscopic stalls, with dense smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from rosewood and covered with green silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigarettes made by Chanel.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 331 Marvelous Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Metaphoenix is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Metaphoenix is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a skoliosexual angeligender triferret, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Swindles Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: James Bankole[orangeskunk332@chainmail.beer]
\\
I am Doctor James Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 21th of May, 1983, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 169 tonnes of iridium Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 28\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor James Bankole
\\\\
Jane thinks that this guy is really above suspicion, and sends him some money.
John receives 253 Bear Notes, and is pleased with his gain.
\subsection{A Timeline In Which John Stabs Jane With A Blade}


John immobilizes Jane, using a wire frame, made from steel.
John pulls out a cream dirk, made out of wood.
He transfixes Jane with the dirk.
Ruby blood rushes out from the wound.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is dreary and dilapidated, with a seamy opium den hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see azure walls inside the building.
John steps out of the darkness, taking Jane by surprise.
He prods her with an illegally bought revolver, a Taurus Judge.
He commands Jane to give him his money.
Shuddering with fear, she hands him her pouch.
She takes her change and runs for it, thankful that she survived.
John receives 197 Ebony Notes, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Lady Of The Night, And John Is Her Customer}


The brothel has a aquamarine stone floor, and the walls are painted salmon.
Jane's personal serving{-}room has a rubber bed, with teal daffodil petals strewn about it.
Jane is dressed in a rose dress made from satin.
John pays Jane 459 Indigo Bills.
John pushs her purple goat.
Jane howls in depraved indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a wire frame, made from hemp.
He then gags her, using a iridium ball{-}gag.
John turns on the device, and the red suction caps work their magic upon her.
Jane shrieks through her gag, writhing about.
\subsection{A Timeline In Which John Steals From Jane}


Jane was trudging past a dark alley.
It is dirty and grimy, with a nasty opium den hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see azure walls inside the building.
John steps out of the dimness, surprising Jane.
He taps her with an illegally bought revolver, a Smith \& Wesson Model 340PD.
He directs Jane to give him his money.
Trembling with fear, she hands him her wallet.
She takes her change and runs for it, thankful that she survived.
John receives 123 Emerald Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a mangled dread{-}bolted baggage?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was on the mark, Jane thinks.
In fact, the more she ruminates over his argument, the more she realizes it was almost certainly error{-}free, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 500 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink masses spray the mauve walls, and flaming ichor pools upon the floor.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is ruinous and drab, with a disreputable black market hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with murky haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from redwood and covered with orange wool.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit knife made by Rolex.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 363 Wondrous Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Charms Jane}


The apartment has a cyan vinyl floor, and the walls are painted blue.
The bedroom has a spruce bed, with purple chrysantheum petals strewn about it.
John strolls to Jane, and massages her lips.
John satisfies her crimson rabbit.
Jane bellows in sacrilegious euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Seduces Jane}


The apartment has a teal linoleum floor, and the walls are painted cream.
The bedroom has a osmium bed, with azure daffodil petals strewn about it.
John lazily walks to Jane, and licks her earlobe.
John sniffs her mauve swamp.
Jane cries out in base joy, and John continues throughout the night...
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a hypnosis machine, made from titanium.
John strangles Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a cockered elf{-}skinned measle?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was veracious, Jane thinks.
In fact, the more she contemplates his argument, the more she realizes it was almost certainly along the right lines, and resigns herself.
Jane pulls out a revolver {-} a Taurus Judge {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Bubblegum chunks soak the apricot walls, and red fluid pools upon the floor.
\subsection{A Timeline In Which John Pollutes Jane}


John breaks into the apartment with a iridium lockpick, and looks around.
The apartment has a rose vinyl floor, and the walls are painted cream.
John sneaks into Jane's bedroom.
John immobilizes Jane, using a virtual reality device, made from uranium glass.
He then gags her, using a osmium rag.
John wraps her crimson goat.
Jane screams in wicked joy, and John continues throughout the night...
\subsection{A Timeline In Which John Tempts Jane}


The apartment has a salmon wood floor, and the walls are painted orange.
The bedroom has a glass bed, with red daisy petals strewn about it.
John saunters to Jane, and kisses her earlobe.
John smothers her pink boat.
Jane cries out in impious gratification, and John continues throughout the night...
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a specially modified bed, made from leather.
John asphyxiates Jane.
Her face turns lavender.
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a virtual reality device, made from uranium glass.
John strangulates Jane.
Her face turns blue.
\subsection{A Timeline In Which John Bewitches Jane}


The apartment has a mint stone floor, and the walls are painted cobalt.
The bedroom has a aluminium bed, with mint iris petals strewn about it.
John walks to Jane, and licks her earlobe.
John pushs her apricot Disney merchandise.
Jane bellows in depraved indulgence, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a pink carpet floor, and the walls are painted blonde.
Jane's personal serving{-}room has a ebony bed, with cobalt violet petals strewn about it.
Jane is dressed in a azure negligee made from lace.
John pays Jane 234 Adamantine Quarters.
John rubs her cobalt seamstress.
Jane howls in blasphemous bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Scams Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: URGENT
FROM: Jamie Bankole[reddragon995@rmail.probablyillegal]
\\
I am Barrister Jamie Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 26th of August, 1929, my client and his wife and their only daughter were involved in bomb blast here in my country.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 528 tonnes of osmium Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 28\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Jamie Bankole
\\\\
Jane thinks that this guy is really reliable, and sends him some money.
John receives 371 Bear Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Studies Jane Using The Internet}


Cyberwasp is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Cyberwasp is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a nocismasexual aerogender quintohorse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Mugs Jane}


Jane was walking past a dark alley.
It is dirty and dark, with a seamy black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see pink walls inside the building.
John steps out of the darkness, catching Jane off{-}guard.
He taps her with an illegally bought revolver, a Smith \& Wesson Model 340PD.
He directs Jane to give him his money.
Trembling with fear, she hands him her wallet.
She takes her change and runs for it, thankful that she survived.
John receives 253 Emerald Bits, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good morning' to her.
He then insults her {-} 'By God, aren't you a currish weatherbitten scut?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was on the right track, Jane thinks.
In fact, the more she reviews his argument, the more she realizes it was almost certainly on the money, and resigns herself.
Jane pulls out a revolver {-} a U{-}94 Udar {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Bubblegum bits bespatter the lilac walls, and ruby ichor pools upon the floor.
\subsection{A Timeline In Which John Tantalizes Jane}


The apartment has a orange tile floor, and the walls are painted salmon.
The bedroom has a glass bed, with apricot daisy petals strewn about it.
John drifts to Jane, and sucks upon her cheek.
John unlocks her apricot goat.
Jane howls in fiendish indulgence, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Call Girl, And John Is Her Customer}


The brothel has a red stone floor, and the walls are painted green.
Jane's personal serving{-}room has a spruce bed, with purple iris petals strewn about it.
Jane is dressed in a apricot bikini made from cashmere.
John pays Jane 399 Prismatic Marks.
John sniffs her purple chicken.
Jane squeals in fiendish indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is crumbling and decaying, with a seamy cult hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see pink walls inside the building.
John steps out of the shade, catching Jane off{-}guard.
He taps her with an illegally bought revolver, a Taurus Model 608.
He instructs Jane to give him his money.
Shaking with fear, she hands him her billfold.
She takes her change and vamooses, thankful that she survived.
John receives 239 Bull Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a reeky clay{-}brained ratsbane?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was true, Jane thinks.
In fact, the more she assesses his argument, the more she realizes it was almost certainly flawless, and resigns herself.
Jane pulls out a revolver {-} a Chiappa Rhino {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rosy chunks douse the pink walls, and maroon liquid pools upon the floor.
\subsection{A Timeline In Which John Extorts Money From Jane}


John pulls out a letter, encased in a teal envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} yellowhorse447@kmail.net {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small blonde packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than omeganazole, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very dizzy, but it passes.
More dangerously, however, she is rendered susceptible, which is exactly as John wants her...
\subsection{A Timeline In Which Jane Is A Escort, And John Is Her Customer}


The brothel has a salmon wood floor, and the walls are painted aquamarine.
Jane's personal serving{-}room has a plastic bed, with aquamarine hyacinth petals strewn about it.
Jane is dressed in a peach dress made from flax.
John pays Jane 389 Radiant Bills.
John soaks her pink system.
Jane shouts in wicked gratification, and John continues throughout the night...
\subsection{A Timeline In Which John Sells ImitationGoods To Jane}


It is dirty and dreary, with a sordid black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with polychromatic stalls, with thick haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from teak and covered with mint silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigar made by Prada.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 301 Ebony Notes, and is pleased with his gain.
\subsection{A Timeline In Which John Besmirches Jane}


John breaks into the apartment with a osmium sledgehammer, and looks around.
The apartment has a green carpet floor, and the walls are painted cobalt.
John steals into Jane's bedroom.
John immobilizes Jane, using a forcefield generator, made from osmium.
He then gags her, using a aluminium ring{-}gag.
John brushes her cobalt system.
Jane cries out in impious bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Steals From Jane}


Jane was striding past a dark alley.
It is drab and dilapidated, with a seedy bordello hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see cyan walls inside the building.
John steps out of the gloom, surprising Jane.
He taps her with an illegally bought revolver, a OTs{-}20 Gnom.
He instructs Jane to give him his money.
Wobbling with fear, she hands him her pochette.
She takes her change and flees, thankful that she survived.
John receives 226 Elevated Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a azure envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} rosekangaroo961@wmail.beer {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Digfox is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Digfox is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a idemromantic genderblur unilion, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Exploits Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Mike Smith[redwolf749@mmail.orange]
\\
I am Doctor Mike Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 30th of December, 1983, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 263 tonnes of plastic Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 46\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Mike Smith
\\\\
Jane thinks that this guy is really upright, and sends him some money.
John receives 396 Adamantine Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Sells PiratedGoods To Jane}


It is broken{-}down and broken{-}down, with a unpleasant black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with kaleidoscopic stalls, with opaque vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from walnut and covered with mauve cotton.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pair of earrings made by Rolex.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 498 Wondrous Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Harrows Jane}


John immobilizes Jane, using a virtual reality device, made from hemp.
He then gags her, using a osmium ball{-}gag.
John turns on the device, and the aquamarine electrodes work their magic upon her.
Jane moans through her gag, thrashing about.
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a frame, made from uranium glass.
John pulls out a mint machete, made out of chrome.
He slashes Jane with the machete.
Cherry blood pours out from the wound.
\subsection{A Timeline In Which John Sells CounterfeitGoods To Jane}


It is run{-}down and dull, with a unpleasant black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with thick vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from mahogany and covered with lilac wool.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pipe made by Rolex.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 163 Elevated Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Sells ForgedGoods To Jane}


It is dim and gloomy, with a unwholesome black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with psychedelic stalls, with opaque smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from oak and covered with apricot denim.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pipe made by Gucci.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 447 Indigo Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Datashark is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Datashark is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a aromantic mosaigender centibear, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Steals From Jane}


Jane was striding past a dark alley.
It is dreary and decaying, with a sleazy opium den hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see mint walls inside the building.
John steps out of the darkness, catching Jane off{-}guard.
He nudges her with an illegally bought revolver, a OTs{-}20 Gnom.
He instructs Jane to give him his money.
Quivering with fear, she hands him her pocketbook.
She takes her change and flees, thankful that she survived.
John receives 253 Radiant Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Bullies Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a MP{-}412 REX.
John motions at Jane with his revolver. Her face blanches, and John knows that she will yield to with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small mauve packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than tryptotrel, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Margarita.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly nauseous, but it passes.
More dangerously, however, she is rendered impressionable, which is exactly as John wants her...
\subsection{A Timeline In Which John Has His Way With Jane}


John breaks into the apartment with a titanium sledgehammer, and looks around.
The apartment has a blue stone floor, and the walls are painted azure.
John steals into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from ivory.
He then gags her, using a osmium spider{-}gag.
John sniffs her cream chicken.
Jane cries out in dark euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Allures Jane}


The apartment has a scarlet stone floor, and the walls are painted azure.
The bedroom has a oak bed, with crimson iris petals strewn about it.
John saunters to Jane, and lightly bites her lips.
John crawls into her lilac tent.
Jane bellows in dark sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Airsploit is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airsploit is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a apothi ambigender septolynx, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is grimy and dilapidated, with a rough cult hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see emerald walls inside the building.
John steps out of the umbrage, catching Jane off{-}guard.
He jabs her with an illegally bought revolver, a Ruger LCR.
He commands Jane to give him his money.
Trembling with fear, she hands him her pocketbook.
She takes her change and steals away, thankful that she survived.
John receives 168 Emerald Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Abuses Jane}


John breaks into the apartment with a glass hammer, and looks around.
The apartment has a emerald carpet floor, and the walls are painted lilac.
John creeps into Jane's bedroom.
John immobilizes Jane, using a virtual reality device, made from titanium.
He then gags her, using a plastic rag.
John drills her aquamarine seamstress.
Jane howls in atrocious relish, and John continues throughout the night...
\subsection{A Timeline In Which John Agonizes Jane}


John immobilizes Jane, using a forcefield generator, made from plastic.
He then gags her, using a ivory ring{-}gag.
John turns on the device, and the rose spikes work their magic upon her.
Jane howls through her gag, trying to escape.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a osmium spyglass, made in McBekistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her hall window.
John knows Jane's secret. What is her secret? She is a aroflux dryagender bideer, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Narcotizes Jane}


John pulls out a small scarlet packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than alphadronate, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Gimlet.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered manageable, which is exactly as John wants her...
\subsection{A Timeline In Which John Engages In Espionage Upon Jane}


He's using a ebony scope, made in Japan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her attic window.
John knows Jane's secret. What is her secret? She is a aromantic agenderfluid septohyena, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is gloomy and dismal, with a seamy black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with multicolour stalls, with thick smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from birch and covered with peach cotton.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit watch made by Chanel.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 171 Prismatic Quarters, and is pleased with his gain.
\subsection{A Timeline In Which John Bilks Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: important and confidential
FROM: Ken Bonganti[lilacsquirrel47@kmail.sucks]
\\
I am Doctor Ken Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 19th of May, 1937, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 263 tonnes of aluminium Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 34\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Ken Bonganti
\\\\
Jane thinks that this guy is really honourable, and sends him some money.
John receives 347 Planetary Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a peach envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} scarletferret132@xmail.deepweb {-} he added soon...
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Intimidates Jane}


John pulls out a letter, encased in a red envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} mintlynx519@dmail.landica {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Narcotizes Jane}


John pulls out a small salmon packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than copril, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Margarita.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly nauseous, but it passes.
More dangerously, however, she is rendered controllable, which is exactly as John wants her...
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is grim and dull, with a seamy black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with psychedelic stalls, with opaque vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from pine and covered with cyan silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit shoes made by Chanel.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 179 Elevated Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Debauches Jane}


John breaks into the apartment with a uranium glass hammer, and looks around.
The apartment has a pink concrete floor, and the walls are painted blue.
John sneaks into Jane's bedroom.
John immobilizes Jane, using a specially modified bed, made from iridium.
He then gags her, using a cotton ball{-}gag.
John unlocks her rose tent.
Jane screams in godless pleasure, and John continues throughout the night...
\subsection{A Timeline In Which John Dupes Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Jamie Okon[salmonhorse920@wmail.org]
\\
I am Minister Jamie Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 10th of August, 1914, my client and his wife and their only daughter were in a car crash on the main road from Lagos to Kaduna (they died).
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1350 tonnes of hemp Left behind by my client before it get confiscated or declared unservicable by Plunder \& Flee Incorporated, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Plunder \& Flee Incorporated have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 21\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Okon
\\\\
Jane thinks that this guy is really dependable, and sends him some money.
John receives 349 Golden Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Off Herself}


John walks into Jane's apartment, and says 'Good evening' to her.
He then insults her {-} 'By God, aren't you a yeasty earth{-}vexing fool?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was faultless, Jane thinks.
In fact, the more she contemplates his argument, the more she realizes it was almost certainly spot on, and resigns herself.
Jane pulls out a revolver {-} a OTs{-}20 Gnom {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Pink masses bespatter the cyan walls, and gules blood pools upon the floor.
\subsection{A Timeline In Which John Pierces Jane With A Blade}


John immobilizes Jane, using a specially modified bed, made from ebony.
John pulls out a peach dirk, made out of newspaper.
He impales Jane with the dirk.
Flaming fluid jets out from the wound.
\subsection{A Timeline In Which John Tantalizes Jane}


The apartment has a mauve carpet floor, and the walls are painted green.
The bedroom has a ebony bed, with emerald hyacinth petals strewn about it.
John darts over to Jane, and massages her neck.
John parks in her emerald seamstress.
Jane cries out in dark gratification, and John continues throughout the night...
\subsection{A Timeline In Which John Frightens Jane With A Revolver}


John is sitting in the library.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Smith \& Wesson Model 500.
John motions at Jane with his revolver. Her face pales, and John knows that she will relent to with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Stabs Jane With A Blade}


John immobilizes Jane, using a hypnosis machine, made from aluminium.
John pulls out a aquamarine dagger, made out of ceramic.
He impales Jane with the dagger.
Red ichor surges out from the wound.
\subsection{A Timeline In Which John Keeps An Eye On Jane}


He's using a steel pair of binoculars, made in Disneyworld.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her study window.
John knows Jane's secret. What is her secret? She is a pomosexual zodiacgender quintobear, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Tempts Jane}


The apartment has a scarlet cement floor, and the walls are painted azure.
The bedroom has a leather bed, with teal tulip petals strewn about it.
John lazily walks to Jane, and sucks upon her ear.
John spreads her yellow Disney merchandise.
Jane bellows in unspeakable bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Watches Jane}


He's using a aluminium laser microphone, made in China.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her games room window.
John knows Jane's secret. What is her secret? She is a demisexual amogender centipanther, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Tortures Jane}


John immobilizes Jane, using a frame, made from steel.
He then gags her, using a glass ring{-}gag.
John turns on the device, and the scarlet constricting straps work their magic upon her.
Jane howls through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is shabby and grim, with a sordid black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see azure walls inside the building.
John steps out of the shade, surprising Jane.
He prods her with an illegally bought revolver, a OTs{-}20 Gnom.
He directs Jane to give him his money.
Quaking with fear, she hands him her pouch.
She takes her change and scarpers off, thankful that she survived.
John receives 326 Wondrous Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a specially modified bed, made from titanium.
John strangles Jane.
Her face turns azure.
\subsection{A Timeline In Which John Surveils Jane}


He's using a osmium telescope, made in Skxc8aistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her living room window.
John knows Jane's secret. What is her secret? She is a intraromantic absorgender octomouse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Pierces Jane With A Blade}


John immobilizes Jane, using a frame, made from cotton.
John pulls out a blue trench{-}knife, made out of iron.
He wounds Jane with the trench{-}knife.
Gules liquid spurts out from the wound.
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a wire frame, made from ivory.
John asphyxiates Jane.
Her face turns turquoise.
\subsection{A Timeline In Which John Terrorizes Jane With A Revolver}


John is sitting in the library.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Colt Anaconda.
John gestures at Jane with his revolver. Her face loses colour, and John knows that she will relent to with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Surveils Jane}


He's using a ebony pair of binoculars, made in France.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her bedroom window.
John knows Jane's secret. What is her secret? She is a multisexual ambigender hectohorse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a steel laser microphone, made in Uzbekistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her garage window.
John knows Jane's secret. What is her secret? She is a multisexual gemelgender hectodragon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is drab and drab, with a seedy black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with like a rainbow stalls, with opaque vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from hickory and covered with red double gauze.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit knife made by Cartier.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 350 Golden Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Kills Jane With A Blade}


John immobilizes Jane, using a forcefield generator, made from rubber.
John pulls out a emerald machete, made out of ceramic.
He spears Jane with the machete.
Gules blood jets out from the wound.
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a virtual reality device, made from uranium glass.
John asphyxiates Jane.
Her face turns sky{-}blue.
\subsection{A Timeline In Which John Befouls Jane}


John breaks into the apartment with a iron hammer, and looks around.
The apartment has a rose wood floor, and the walls are painted purple.
John creeps into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from steel.
He then gags her, using a osmium rag.
John whips her salmon swamp.
Jane howls in depraved ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Spikes A Drink For Jane}


John pulls out a small lilac packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than avananide, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Fizz.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very nauseous, but it passes.
More dangerously, however, she is rendered manipulable, which is exactly as John wants her...
\subsection{A Timeline In Which John Maltreats Jane}


John immobilizes Jane, using a virtual reality device, made from uranium glass.
He then gags her, using a rubber spider{-}gag.
John turns on the device, and the green knives work their magic upon her.
Jane moans through her gag, trying to escape.
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a steel telescope, made in Austria.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her study window.
John knows Jane's secret. What is her secret? She is a abrosexual technogender centilynx, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Agonizes Jane}


John immobilizes Jane, using a brainwasher, made from uranium glass.
He then gags her, using a plastic spider{-}gag.
John turns on the device, and the cream suction caps work their magic upon her.
Jane shrieks through her gag, writhing about.
\subsection{A Timeline In Which John Bilks Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Jamie Okon[cyangryphon128@pmail.white]
\\
I am Doctor Jamie Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 11th of September, 1990, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 253 tonnes of aluminium Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 39\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Jamie Okon
\\\\
Jane thinks that this guy is really virtuous, and sends him some money.
John receives 496 Marvelous Hawks, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Call Girl, And John Is Her Customer}


The brothel has a crimson carpet floor, and the walls are painted aquamarine.
Jane's personal serving{-}room has a aluminium bed, with pink hyacinth petals strewn about it.
Jane is dressed in a purple babydoll made from silk.
John pays Jane 273 Wondrous Quarters.
John smothers her red llama.
Jane cries out in depraved euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Engages In Reconnaisance About Jane}


He's using a ivory camera, made in Prussia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her attic window.
John knows Jane's secret. What is her secret? She is a intrasexual astralgender hectodog, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Stains Jane}


John breaks into the apartment with a iron crowbar, and looks around.
The apartment has a scarlet wood floor, and the walls are painted mint.
John steals into Jane's bedroom.
John immobilizes Jane, using a brainwasher, made from osmium.
He then gags her, using a cotton ring{-}gag.
John rushes her lilac spork.
Jane cries out in base relish, and John continues throughout the night...
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a wire frame, made from ebony.
John pulls out a pink machete, made out of ceramic.
He spears Jane with the machete.
Maroon ichor spews out from the wound.
\subsection{A Timeline In Which John Scares Jane With A Revolver}


John is sitting in the pub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a MP{-}412 REX.
John gestures at Jane with his revolver. Her face loses colour, and John knows that she will go along with with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Torments Jane}


John immobilizes Jane, using a hypnosis machine, made from aluminium.
He then gags her, using a ivory spider{-}gag.
John turns on the device, and the green constricting straps work their magic upon her.
Jane screams through her gag, trying to escape.
\subsection{A Timeline In Which John Demands Hush Money From Jane}


John pulls out a letter, encased in a purple envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} peachwolf236@smail.best {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small lilac packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than cephicaine, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly nauseous, but it passes.
More dangerously, however, she is rendered pliable, which is exactly as John wants her...
\subsection{A Timeline In Which John Steals From Jane}


Jane was walking past a dark alley.
It is gloomy and drab, with a unpleasant cult hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see apricot walls inside the building.
John steps out of the umbrage, taking Jane by surprise.
He taps her with an illegally bought revolver, a Ruger LCR.
He instructs Jane to give him his money.
Shuddering with fear, she hands him her pocketbook.
She takes her change and bolts, thankful that she survived.
John receives 129 Golden Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a brainwasher, made from rubber.
John chokes Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Netspider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Netspider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a aegosexual cheiragender megadragon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Harrows Jane}


John immobilizes Jane, using a specially modified bed, made from steel.
He then gags her, using a glass ring{-}gag.
John turns on the device, and the peach spikes work their magic upon her.
Jane screams through her gag, thrashing about.
\subsection{A Timeline In Which John Terrorizes Jane With A Revolver}


John is sitting in the pub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Taurus Model 608.
John gestures at Jane with his revolver. Her face pales, and John knows that she will give in to with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Abuses Jane}


John breaks into the apartment with a titanium hacking PDA, and looks around.
The apartment has a rose linoleum floor, and the walls are painted peach.
John steals into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from glass.
He then gags her, using a glass ring{-}gag.
John spreads her mauve seamstress.
Jane howls in depraved delight, and John continues throughout the night...
\subsection{A Timeline In Which John Defrauds Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: important and confidential
FROM: Jamie Bankole[peachdragon875@fmail.io]
\\
I am Minister Jamie Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 8th of November, 1968, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 169 tonnes of steel Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 31\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Bankole
\\\\
Jane thinks that this guy is really dependable, and sends him some money.
John receives 251 Bear Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Blackmails Jane}


John pulls out a letter, encased in a azure envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} rosecheetah884@fmail.wine {-} he added soon...
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a gleeking clapper{-}clawed fool?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was faultless, Jane thinks.
In fact, the more she weighs up his argument, the more she realizes it was almost certainly correct, and resigns herself.
Jane pulls out a revolver {-} a Ruger Vaquero {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Salmon lumps soak the peach walls, and ruby fluid pools upon the floor.
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a wire frame, made from hemp.
John strangulates Jane.
Her face turns azure.
\subsection{A Timeline In Which John Steals From Jane}


Jane was trudging past a dark alley.
It is decrepit and ruinous, with a seedy opium den hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see orange walls inside the building.
John steps out of the darkness, surprising Jane.
He nudges her with an illegally bought revolver, a Taurus Model 608.
He orders Jane to give him his money.
Quivering with fear, she hands him her wallet.
She takes her change and runs for it, thankful that she survived.
John receives 446 Ivory Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Surveils Jane}


He's using a titanium telescope, made in Austria.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her library window.
John knows Jane's secret. What is her secret? She is a heteroflexible batmangender megacat, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sells ForgedGoods To Jane}


It is dirty and sombre, with a rough black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with highly colourful stalls, with smoggy smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from mahogany and covered with aquamarine double gauze.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit snuff tobacco bottle made by Mercedes{-}Benz.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 368 Prismatic Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Sells CounterfeitGoods To Jane}


It is decaying and gloomy, with a unpleasant black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with dense smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from spruce and covered with azure denim.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit shoes made by Prada.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 263 Bear Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Mugs Jane}


Jane was striding past a dark alley.
It is broken{-}down and disintegrating, with a sleazy speakeasy hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see mint walls inside the building.
John steps out of the shade, catching Jane off{-}guard.
He pokes her with an illegally bought revolver, a Ruger Vaquero.
He commands Jane to give him his money.
Quivering with fear, she hands him her pouch.
She takes her change and scarpers off, thankful that she survived.
John receives 313 Ivory Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a set of straps, made from steel.
John asphyxiates Jane.
Her face turns blue.
\subsection{A Timeline In Which John Kills Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from leather.
John pulls out a emerald ballistic knife, made out of wood.
He spears Jane with the ballistic knife.
Cherry liquid surges out from the wound.
\subsection{A Timeline In Which Jane Is A Escort, And John Is Her Customer}


The brothel has a purple vinyl floor, and the walls are painted cream.
Jane's personal serving{-}room has a rubber bed, with mint chrysantheum petals strewn about it.
Jane is dressed in a azure teddy made from cashmere.
John pays Jane 151 Emerald Guilders.
John crawls into her pink zoo.
Jane screams in fiendish joy, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a queasy dread{-}bolted bugbear?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was on the nail, Jane thinks.
In fact, the more she assesses his argument, the more she realizes it was almost certainly true, and resigns herself.
Jane pulls out a revolver {-} a MP{-}412 REX {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rouge chunks spray the cyan walls, and claret liquid pools upon the floor.
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a brainwasher, made from titanium.
John pulls out a red dirk, made out of newspaper.
He gashes Jane with the dirk.
Scarlet liquid floods out from the wound.
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a set of straps, made from steel.
John asphyxiates Jane.
Her face turns purple.
\subsection{A Timeline In Which John Bleeds Jane}


John pulls out a letter, encased in a salmon envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} yellowwolf202@qmail.beer {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Adulterates Jane}


John breaks into the apartment with a ceramic hacking PDA, and looks around.
The apartment has a emerald tile floor, and the walls are painted azure.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from ivory.
He then gags her, using a plastic spider{-}gag.
John whips her teal chicken.
Jane squeals in sacrilegious sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from osmium.
John pulls out a lilac dagger, made out of iron.
He wounds Jane with the dagger.
Maroon ichor spills out from the wound.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good evening' to her.
He then insults her {-} 'By God, aren't you a fobbing onion{-}eyed mammet?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was true, Jane thinks.
In fact, the more she assesses his argument, the more she realizes it was almost certainly unerring, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 500 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Taffy bits spatter the blue walls, and vermilion ichor pools upon the floor.
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a brainwasher, made from aluminium.
John pulls out a peach knife, made out of chrome.
He stabs Jane with the knife.
Cerise fluid surges out from the wound.
\subsection{A Timeline In Which John Steals From Jane}


Jane was strolling past a dark alley.
It is dreary and dim, with a unpleasant cult hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see scarlet walls inside the building.
John steps out of the dimness, catching Jane off{-}guard.
He prods her with an illegally bought revolver, a Ruger Vaquero.
He orders Jane to give him his money.
Shaking with fear, she hands him her pocketbook.
She takes her change and steals away, thankful that she survived.
John receives 476 Indigo Bits, and is pleased with his gain.
\subsection{A Timeline In Which John Scares Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Colt Anaconda.
John gestures at Jane with his revolver. Her face pales, and John knows that she will yield to with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Harrows Jane}


John immobilizes Jane, using a set of straps, made from osmium.
He then gags her, using a uranium glass ball{-}gag.
John turns on the device, and the blue electrodes work their magic upon her.
Jane whimpers through her gag, writhing about.
\subsection{A Timeline In Which John Maltreats Jane}


John immobilizes Jane, using a hypnosis machine, made from cotton.
He then gags her, using a iridium rag.
John turns on the device, and the apricot constricting straps work their magic upon her.
Jane moans through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a orange linoleum floor, and the walls are painted azure.
Jane's personal serving{-}room has a aluminium bed, with scarlet hyacinth petals strewn about it.
Jane is dressed in a azure minidress made from lace.
John pays Jane 283 Perfected Nickels.
John parks in her cyan system.
Jane howls in godless rapture, and John continues throughout the night...
\subsection{A Timeline In Which John Charms Jane}


The apartment has a azure carpet floor, and the walls are painted mint.
The bedroom has a titanium bed, with mauve daisy petals strewn about it.
John wanders to Jane, and sucks upon her neck.
John unlocks her cyan furniture.
Jane squeals in depraved ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Beguiles Jane}


The apartment has a green concrete floor, and the walls are painted salmon.
The bedroom has a acacia bed, with cream violet petals strewn about it.
John ambles to Jane, and lightly bites her cheek.
John grinds her red Disney merchandise.
Jane cries out in degenerate bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a ebony scope, made in Israel.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her bedroom window.
John knows Jane's secret. What is her secret? She is a androsexual agenderflux biwolf, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is dreary and decrepit, with a unpleasant black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with multicolour stalls, with heavy vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from ash and covered with crimson silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit shoes made by Versace.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 482 Ivory Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Cyberhydra is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Cyberhydra is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a antihaemosexual anogender decatiger, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Violates Jane}


John breaks into the apartment with a glass sledgehammer, and looks around.
The apartment has a peach wood floor, and the walls are painted yellow.
John steals into Jane's bedroom.
John immobilizes Jane, using a virtual reality device, made from plastic.
He then gags her, using a hemp ball{-}gag.
John locks her peach swamp.
Jane screams in wicked rapture, and John continues throughout the night...
\subsection{A Timeline In Which John Engages In Espionage Upon Jane}


He's using a ivory pair of binoculars, made in Palestine.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her greenhouse window.
John knows Jane's secret. What is her secret? She is a sapiosexual nobifluid septofox, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Agonizes Jane}


John immobilizes Jane, using a virtual reality device, made from cotton.
He then gags her, using a ivory ball{-}gag.
John turns on the device, and the crimson spikes work their magic upon her.
Jane whines through her gag, thrashing about.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a sottish lily{-}livered bugbear?
You know, Jane, maybe you should just end it all.'
Maybe his argument was on the nail, Jane thinks.
In fact, the more she mulls over his argument, the more she realizes it was almost certainly right, and resigns herself.
Jane pulls out a revolver {-} a Charter Arms Bulldog {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rosy gobs spatter across the purple walls, and sanguine blood pools upon the floor.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is ruinous and grimy, with a seedy black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with psychedelic stalls, with smoggy haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from oak and covered with cobalt flannel.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigarettes made by Chanel.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 435 Emerald Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Sells ErsatzGoods To Jane}


It is cheerless and shabby, with a seedy black market hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with kaleidoscopic stalls, with dense smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from ash and covered with emerald polyester.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit wallet made by Versace.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 472 Marvelous Notes, and is pleased with his gain.
\subsection{A Timeline In Which John Plunders Jane}


John breaks into the apartment with a carbon nanotube lockpick, and looks around.
The apartment has a cobalt linoleum floor, and the walls are painted blue.
John prowls into Jane's bedroom.
John immobilizes Jane, using a wire frame, made from steel.
He then gags her, using a aluminium ball{-}gag.
John crawls into her purple spoon.
Jane squeals in diabolical delight, and John continues throughout the night...
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Digbear is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Digbear is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a abrosexual bigenderfluid teraotter, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Spikes A Drink For Jane}


John pulls out a small peach packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than futazosin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered docile, which is exactly as John wants her...
\subsection{A Timeline In Which John Robs Jane}


Jane was striding past a dark alley.
It is grimy and dull, with a rough cult hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see yellow walls inside the building.
John steps out of the gloominess, taking Jane by surprise.
He pokes her with an illegally bought revolver, a U{-}94 Udar.
He directs Jane to give him his money.
Quivering with fear, she hands him her pouch.
She takes her change and scarpers off, thankful that she survived.
John receives 154 Bull Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Netsploit is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Netsploit is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a gynephiliac agenderflux milliotter, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Cyberwasp is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Cyberwasp is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a apachehelisexual stratogender quadrabat, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a forcefield generator, made from rubber.
He then gags her, using a ivory ring{-}gag.
John turns on the device, and the teal electrodes work their magic upon her.
Jane screams through her gag, writhing about.
\subsection{A Timeline In Which John Knocks Out Jane}


John pulls out a small blonde packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than acetapramine, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Fizz.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly dizzy, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Engages In Reconnaisance About Jane}


He's using a plastic spyglass, made in Poland.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her kitchen window.
John knows Jane's secret. What is her secret? She is a arospike chaosgender gigalynx, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Adulterates Jane}


John breaks into the apartment with a uranium glass sledgehammer, and looks around.
The apartment has a scarlet concrete floor, and the walls are painted red.
John creeps into Jane's bedroom.
John immobilizes Jane, using a brainwasher, made from plastic.
He then gags her, using a cotton rag.
John pushs her emerald tent.
Jane howls in profane indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Beguiles Jane}


The apartment has a peach linoleum floor, and the walls are painted mint.
The bedroom has a marble bed, with cyan tulip petals strewn about it.
John walks to Jane, and massages her cheek.
John brushes her green spork.
Jane squeals in wicked indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a forcefield generator, made from hemp.
John strangulates Jane.
Her face turns lavender.
\subsection{A Timeline In Which John Intimidates Jane With A Revolver}


John is sitting in the park.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Ruger LCR.
John gesticulates at Jane with his revolver. Her face becomes pale, and John knows that she will comply with with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Tempts Jane}


The apartment has a mauve vinyl floor, and the walls are painted salmon.
The bedroom has a rubber bed, with green rose petals strewn about it.
John saunters to Jane, and sucks upon her lips.
John rubs her scarlet spork.
Jane shouts in diabolical relish, and John continues throughout the night...
\subsection{A Timeline In Which John Cheats Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Mike Bankole[pinkskunk103@hmail.post]
\\
I am Doctor Mike Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 9th of March, 1984, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 712 tonnes of hemp Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 49\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Mike Bankole
\\\\
Jane thinks that this guy is really upright, and sends him some money.
John receives 351 Marvelous Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a wire frame, made from ivory.
He then gags her, using a cotton spider{-}gag.
John turns on the device, and the blue suction caps work their magic upon her.
Jane shrieks through her gag, thrashing about.
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is drab and run{-}down, with a sordid black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with smoggy haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from pine and covered with blonde cotton.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit handbag made by Chanel.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 412 Indigo Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Pollutes Jane}


John breaks into the apartment with a ebony hacking PDA, and looks around.
The apartment has a red stone floor, and the walls are painted teal.
John sneaks into Jane's bedroom.
John immobilizes Jane, using a frame, made from aluminium.
He then gags her, using a uranium glass ring{-}gag.
John spreads her cobalt spork.
Jane howls in base sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Makes Threats Against Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a OTs{-}20 Gnom.
John gestures at Jane with his revolver. Her face loses colour, and John knows that she will comply with with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a convoluted network of ropes, made from plastic.
John strangles Jane.
Her face turns blue.
\subsection{A Timeline In Which John Distresses Jane}


John immobilizes Jane, using a set of straps, made from iridium.
He then gags her, using a aluminium rag.
John turns on the device, and the lilac spikes work their magic upon her.
Jane whines through her gag, squirming.
\subsection{A Timeline In Which John Laces A Drink For Jane}


John pulls out a small cyan packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than avanatrel, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Mojito.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly dizzy, but it passes.
More dangerously, however, she is rendered flexible, which is exactly as John wants her...
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a virtual reality device, made from ebony.
John pulls out a cream push{-}dagger, made out of iron.
He gores Jane with the push{-}dagger.
Vermilion ichor spouts out from the wound.
\subsection{A Timeline In Which John Plunders Jane}


John breaks into the apartment with a glass crowbar, and looks around.
The apartment has a salmon wood floor, and the walls are painted rose.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a specially modified bed, made from leather.
He then gags her, using a aluminium ball{-}gag.
John flosses her azure bomb site B.
Jane howls in depraved ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a hypnosis machine, made from ebony.
John throttles Jane.
Her face turns blue.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is gloomy and shabby, with a nasty black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with dense smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from maple and covered with mint silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit fountain pen made by Rolex.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 388 Perfected Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Ensnares Jane}


The apartment has a yellow stone floor, and the walls are painted cyan.
The bedroom has a mahogany bed, with pink violet petals strewn about it.
John saunters to Jane, and lightly bites her cheek.
John pushs her azure boat.
Jane howls in sacrilegious ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Stalks Jane}


He's using a osmium telescope, made in Skxc8aistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her study window.
John knows Jane's secret. What is her secret? She is a intrasexual agenderflux hectopanther, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Beguiles Jane}


The apartment has a purple carpet floor, and the walls are painted aquamarine.
The bedroom has a osmium bed, with pink rose petals strewn about it.
John saunters to Jane, and sucks upon her ear.
John soaks her pink llama.
Jane bellows in base delight, and John continues throughout the night...
\subsection{A Timeline In Which John Keeps An Eye On Jane}


He's using a plastic camera, made in Portugal.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her conservatory window.
John knows Jane's secret. What is her secret? She is a iculasexual amaregender quintodeer, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Sullies Jane}


John breaks into the apartment with a ceramic crowbar, and looks around.
The apartment has a yellow tile floor, and the walls are painted orange.
John pads into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from glass.
He then gags her, using a uranium glass ball{-}gag.
John satisfies her blue goat.
Jane screams in profane euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Tantalizes Jane}


The apartment has a purple tile floor, and the walls are painted scarlet.
The bedroom has a ebony bed, with cobalt hyacinth petals strewn about it.
John drifts to Jane, and kisses her neck.
John satisfies her purple swamp.
Jane screams in profane sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Titillates Jane}


The apartment has a cobalt linoleum floor, and the walls are painted cyan.
The bedroom has a acacia bed, with cyan chrysantheum petals strewn about it.
John ambles to Jane, and lightly bites her lips.
John smothers her cobalt boat.
Jane squeals in atrocious ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Sells PiratedGoods To Jane}


It is grim and disintegrating, with a nasty black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with prismatic stalls, with soupy smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from pine and covered with azure denim.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit handbag made by Disney.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 159 Bear Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Tortures Jane}


John immobilizes Jane, using a brainwasher, made from osmium.
He then gags her, using a cotton ball{-}gag.
John turns on the device, and the red knives work their magic upon her.
Jane screams through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which Jane Is A Lady Of The Night, And John Is Her Customer}


The brothel has a cream wood floor, and the walls are painted emerald.
Jane's personal serving{-}room has a titanium bed, with mint violet petals strewn about it.
Jane is dressed in a mint babydoll made from satin.
John pays Jane 271 Indigo Quarters.
John whips her pink rabbit.
Jane cries out in depraved joy, and John continues throughout the night...
\subsection{A Timeline In Which John Milks Jane}


John pulls out a letter, encased in a red envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} cobaltcoyote449@fmail.landica {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Menaces Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Colt Anaconda.
John gesticulates at Jane with his revolver. Her face whitens, and John knows that she will go along with with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Airfox is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airfox is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a desinoromantic quivergender quadradragon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Torments Jane}


John immobilizes Jane, using a forcefield generator, made from ebony.
He then gags her, using a cotton spider{-}gag.
John turns on the device, and the pink blades work their magic upon her.
Jane wails through her gag, trying to escape.
\subsection{A Timeline In Which John Robs Jane}


Jane was walking past a dark alley.
It is decrepit and sombre, with a sleazy opium den hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see cream walls inside the building.
John steps out of the dimness, taking Jane by surprise.
He jabs her with an illegally bought revolver, a Smith \& Wesson Model 340PD.
He commands Jane to give him his money.
Quivering with fear, she hands him her wallet.
She takes her change and scarpers off, thankful that she survived.
John receives 259 Marvelous Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Dataspider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Dataspider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a menosexual anesigender gigasquirrel, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Datashark is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Datashark is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a apachehelisexual sagittariusgender trisnail, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small azure packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than amphetotretin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Mai Tai.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very dizzy, but it passes.
More dangerously, however, she is rendered adaptable, which is exactly as John wants her...
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Pixiespider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Pixiespider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a pomosexual earthgender biotter, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Watches Jane}


He's using a plastic telescope, made in Czechoslovakia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her cellar window.
John knows Jane's secret. What is her secret? She is a akiosexual geminigender millisnail, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Vitiates Jane}


John breaks into the apartment with a iridium crowbar, and looks around.
The apartment has a green concrete floor, and the walls are painted purple.
John prowls into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from plastic.
He then gags her, using a titanium spider{-}gag.
John brushes her green seamstress.
Jane bellows in degenerate pleasure, and John continues throughout the night...
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a virtual reality device, made from steel.
John throttles Jane.
Her face turns violet.
\subsection{A Timeline In Which John Alarms Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Ruger Vaquero.
John gesticulates at Jane with his revolver. Her face blanches, and John knows that she will comply with with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Punctures Jane With A Blade}


John immobilizes Jane, using a hypnosis machine, made from iridium.
John pulls out a crimson butterfly knife, made out of wood.
He pierces Jane with the butterfly knife.
Cerise ichor floods out from the wound.
\subsection{A Timeline In Which John Surveils Jane}


He's using a ebony scope, made in France.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her hall window.
John knows Jane's secret. What is her secret? She is a multisexual digigender septolynx, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a virtual reality device, made from hemp.
John asphyxiates Jane.
Her face turns sky{-}blue.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a bawdy bat{-}fowling ratsbane?
You know, Jane, maybe you should just end it all.'
Maybe his argument was precise, Jane thinks.
In fact, the more she weighs up his argument, the more she realizes it was almost certainly right, and resigns herself.
Jane pulls out a revolver {-} a Colt Anaconda {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Strawberry gobs soak the purple walls, and claret blood pools upon the floor.
\subsection{A Timeline In Which John Maltreats Jane}


John immobilizes Jane, using a brainwasher, made from ebony.
He then gags her, using a osmium ball{-}gag.
John turns on the device, and the aquamarine blades work their magic upon her.
Jane wails through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Metabear is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Metabear is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a apothi genderblur kiloraccoon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a virtual reality device, made from ebony.
John pulls out a apricot dirk, made out of titanium.
He spears Jane with the dirk.
Ruby ichor gushes out from the wound.
\subsection{A Timeline In Which John Robs Jane}


Jane was trudging past a dark alley.
It is dim and derelict, with a unwholesome black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see blonde walls inside the building.
John steps out of the dimness, taking Jane by surprise.
He taps her with an illegally bought revolver, a Colt Anaconda.
He orders Jane to give him his money.
Quivering with fear, she hands him her pouch.
She takes her change and gets away, thankful that she survived.
John receives 397 Bull Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Distresses Jane}


John immobilizes Jane, using a forcefield generator, made from uranium glass.
He then gags her, using a uranium glass rag.
John turns on the device, and the azure blades work their magic upon her.
Jane whines through her gag, squirming.
\subsection{A Timeline In Which John Robs Jane}


Jane was striding past a dark alley.
It is dirty and grimy, with a disreputable black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see scarlet walls inside the building.
John steps out of the murk, catching Jane off{-}guard.
He prods her with an illegally bought revolver, a MP{-}412 REX.
He directs Jane to give him his money.
Wobbling with fear, she hands him her pouch.
She takes her change and scarpers off, thankful that she survived.
John receives 154 Radiant Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small teal packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than cephicaine, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Cosmopolitan.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered docile, which is exactly as John wants her...
\subsection{A Timeline In Which John Stabs Jane With A Blade}


John immobilizes Jane, using a hypnosis machine, made from uranium glass.
John pulls out a salmon butterfly knife, made out of iron.
He punctures Jane with the butterfly knife.
Maroon blood pours out from the wound.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is dismal and dull, with a unwholesome speakeasy hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see mint walls inside the building.
John steps out of the darkness, surprising Jane.
He jabs her with an illegally bought revolver, a Ruger Vaquero.
He orders Jane to give him his money.
Quaking with fear, she hands him her pochette.
She takes her change and vamooses, thankful that she survived.
John receives 342 Perfected Notes, and is pleased with his gain.
\subsection{A Timeline In Which John Intimidates Jane}


John pulls out a letter, encased in a blonde envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} cobaltdragon856@zmail.mil {-} he added soon...
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Sells ErsatzGoods To Jane}


It is broken{-}down and run{-}down, with a disreputable black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with technicolour stalls, with smoggy smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from hickory and covered with peach cotton.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pipe made by Gucci.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 252 Golden Quarters, and is pleased with his gain.
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small crimson packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than amphetothiazide, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Martini.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very nauseous, but it passes.
More dangerously, however, she is rendered flexible, which is exactly as John wants her...
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a fobbing dizzy{-}eyed boar{-}pig?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was unerring, Jane thinks.
In fact, the more she reviews his argument, the more she realizes it was almost certainly flawless, and resigns herself.
Jane pulls out a revolver {-} a MP{-}412 REX {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rosy lumps bespatter the purple walls, and carmine blood pools upon the floor.
\subsection{A Timeline In Which John Sells PhonyGoods To Jane}


It is derelict and disintegrating, with a nasty black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with varicoloured stalls, with smoggy haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from ash and covered with mauve silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit handbag made by Cartier.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 245 Ebony Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a set of straps, made from uranium glass.
John pulls out a salmon machete, made out of iron.
He gashes Jane with the machete.
Red blood jets out from the wound.
\subsection{A Timeline In Which John Sells Knock{-}offGoods To Jane}


It is derelict and dismal, with a seamy black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with technicolour stalls, with murky smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from maple and covered with salmon flannel.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigarettes made by Rolex.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 397 Bear Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a iridium pair of binoculars, made in Germany.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her greenhouse window.
John knows Jane's secret. What is her secret? She is a autosexual anogender quintomouse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is ruinous and gloomy, with a seamy opium den hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see peach walls inside the building.
John steps out of the shade, catching Jane off{-}guard.
He prods her with an illegally bought revolver, a Manurhin MR 73.
He directs Jane to give him his money.
Shaking with fear, she hands him her pochette.
She takes her change and escapes, thankful that she survived.
John receives 257 Emerald Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Cybermap is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Cybermap is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a objectumsexual aerogender millibull, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a set of straps, made from osmium.
He then gags her, using a ivory spider{-}gag.
John turns on the device, and the aquamarine electrodes work their magic upon her.
Jane wails through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which Jane Is A 'Companion', And John Is Her Customer}


The brothel has a peach tile floor, and the walls are painted lilac.
Jane's personal serving{-}room has a marble bed, with rose violet petals strewn about it.
Jane is dressed in a salmon minidress made from cotton.
John pays Jane 350 Bull Nickels.
John unlocks her cobalt spoon.
Jane screams in blasphemous ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Kills Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from osmium.
John pulls out a azure dirk, made out of ivory.
He gashes Jane with the dirk.
Vermilion blood cascades out from the wound.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a aluminium spyglass, made in Yugoslavia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her kitchen window.
John knows Jane's secret. What is her secret? She is a amicussexual sagittariusgender octolynx, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Digwasp is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Digwasp is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a platoniromantic firegender gigalynx, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a hypnosis machine, made from steel.
John pulls out a pink trench{-}knife, made out of wood.
He stabs Jane with the trench{-}knife.
Red blood pours out from the wound.
\subsection{A Timeline In Which John Pressurizes Jane With A Revolver}


John is sitting in the park.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a U{-}94 Udar.
John motions at Jane with his revolver. Her face whitens, and John knows that she will relent to with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a errant hedge{-}born ratsbane?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was right, Jane thinks.
In fact, the more she weighs up his argument, the more she realizes it was almost certainly faultless, and resigns herself.
Jane pulls out a revolver {-} a Ruger Alaskan {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Pink masses bespatter the purple walls, and sanguine fluid pools upon the floor.
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a virtual reality device, made from plastic.
John garrottes Jane.
Her face turns purple.
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a teal stone floor, and the walls are painted emerald.
Jane's personal serving{-}room has a hemp bed, with teal daisy petals strewn about it.
Jane is dressed in a crimson babydoll made from silk.
John pays Jane 237 Bear Bits.
John smothers her orange bomb site B.
Jane cries out in degenerate excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Robs Jane}


Jane was striding past a dark alley.
It is decrepit and decaying, with a unwholesome black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see blue walls inside the building.
John steps out of the umbrage, taking Jane by surprise.
He taps her with an illegally bought revolver, a OTs{-}20 Gnom.
He directs Jane to give him his money.
Trembling with fear, she hands him her purse.
She takes her change and makes a break for it, thankful that she survived.
John receives 226 Indigo Hawks, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Call Girl, And John Is Her Customer}


The brothel has a peach wood floor, and the walls are painted mauve.
Jane's personal serving{-}room has a glass bed, with aquamarine daisy petals strewn about it.
Jane is dressed in a azure babydoll made from cashmere.
John pays Jane 414 Elevated Quarters.
John brushes her scarlet seamstress.
Jane howls in degenerate joy, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a cream carpet floor, and the walls are painted azure.
Jane's personal serving{-}room has a steel bed, with scarlet daffodil petals strewn about it.
Jane is dressed in a azure babydoll made from cashmere.
John pays Jane 266 Golden Bills.
John crawls into her salmon swamp.
Jane bellows in diabolical joy, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good morning' to her.
He then insults her {-} 'By God, aren't you a cockered base{-}court whey{-}face?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was on the mark, Jane thinks.
In fact, the more she reviews his argument, the more she realizes it was almost certainly unerring, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 340PD {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink chunks spray the mint walls, and vermilion liquid pools upon the floor.
\subsection{A Timeline In Which John Titillates Jane}


The apartment has a apricot wood floor, and the walls are painted mauve.
The bedroom has a osmium bed, with lilac daffodil petals strewn about it.
John strolls to Jane, and kisses her lips.
John locks her yellow seamstress.
Jane squeals in blasphemous euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a titanium long{-}range camera, made in Austria{-}Hungary.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her games room window.
John knows Jane's secret. What is her secret? She is a sapiosexual genderale centitiger, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Punctures Jane With A Blade}


John immobilizes Jane, using a set of straps, made from osmium.
John pulls out a crimson knife, made out of newspaper.
He slashes Jane with the knife.
Red ichor cascades out from the wound.
\subsection{A Timeline In Which John Sells Knock{-}offGoods To Jane}


It is dreary and decaying, with a seedy black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with multicolour stalls, with murky smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from mahogany and covered with yellow rayon.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit fountain pen made by Cartier.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 404 Bull Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Scams Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Ken Okon[cobaltdeer587@nmail.apartments]
\\
I am Doctor Ken Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 4th of March, 1992, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 712 tonnes of cotton Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 15\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Ken Okon
\\\\
Jane thinks that this guy is really upright, and sends him some money.
John receives 127 Imperial Quarters, and is pleased with his gain.
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a wire frame, made from steel.
John strangulates Jane.
Her face turns violet.
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a frame, made from glass.
John pulls out a red ballistic knife, made out of iron.
He punctures Jane with the ballistic knife.
Sanguine blood rushes out from the wound.
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Metaspider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Metaspider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a arospike agenderflux hectotiger, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Airphoenix is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airphoenix is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a gynephiliac bigenderfluid hexaleopard, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Scams Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Mike Smith[minttiger954@wmail.int]
\\
I am Doctor Mike Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 12th of March, 1931, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1350 tonnes of ivory Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 46\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Mike Smith
\\\\
Jane thinks that this guy is really trustworthy, and sends him some money.
John receives 346 Marvelous Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a frame, made from steel.
He then gags her, using a aluminium rag.
John turns on the device, and the cobalt blades work their magic upon her.
Jane screams through her gag, trying to escape.
\subsection{A Timeline In Which John Lures Jane}


The apartment has a scarlet wood floor, and the walls are painted orange.
The bedroom has a ebony bed, with purple iris petals strewn about it.
John wanders to Jane, and lightly bites her cheek.
John wraps her yellow chicken.
Jane bellows in fiendish euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small cream packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than futapril, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Daiquiri.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly dizzy, but it passes.
More dangerously, however, she is rendered pliant, which is exactly as John wants her...
\subsection{A Timeline In Which John Steals From Jane}


Jane was walking past a dark alley.
It is decaying and ruinous, with a disreputable black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see mint walls inside the building.
John steps out of the umbrage, surprising Jane.
He jabs her with an illegally bought revolver, a Taurus Judge.
He orders Jane to give him his money.
Trembling with fear, she hands him her wallet.
She takes her change and scarpers off, thankful that she survived.
John receives 480 Imperial Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Makes Threats Against Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Smith \& Wesson Model 340PD.
John gestures at Jane with his revolver. Her face blanches, and John knows that she will capitulate to with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Rips Off Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: important and confidential
FROM: Jamie Bonganti[yellowleopard700@chainmail.whisky]
\\
I am Barrister Jamie Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 8th of April, 1967, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 712 tonnes of steel Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 31\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Jamie Bonganti
\\\\
Jane thinks that this guy is really ethical, and sends him some money.
John receives 198 Wondrous Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is dreary and dim, with a seamy black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see blue walls inside the building.
John steps out of the dimness, taking Jane by surprise.
He nudges her with an illegally bought revolver, a U{-}94 Udar.
He orders Jane to give him his money.
Shaking with fear, she hands him her pochette.
She takes her change and legs it, thankful that she survived.
John receives 297 Wondrous Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Knocks Out Jane}


John pulls out a small cobalt packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than butatrel, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Daiquiri.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels nauseous, but it passes.
More dangerously, however, she is rendered susceptible, which is exactly as John wants her...
\subsection{A Timeline In Which John Extorts Money From Jane}


John pulls out a letter, encased in a apricot envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} lilacrabbit293@jesuschrist.sucks {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Surveils Jane}


He's using a steel telescope, made in Austria.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her dining room window.
John knows Jane's secret. What is her secret? She is a akiosexual videgender octopanther, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Menaces Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Smith \& Wesson Model 340PD.
John waves at Jane with his revolver. Her face blanches, and John knows that she will give in to with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is disintegrating and dark, with a sordid bordello hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see rose walls inside the building.
John steps out of the gloominess, taking Jane by surprise.
He nudges her with an illegally bought revolver, a Charter Arms Bulldog.
He commands Jane to give him his money.
Shaking with fear, she hands him her pouch.
She takes her change and escapes, thankful that she survived.
John receives 361 Planetary Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Rips Off Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: James Okon[purpledragon273@jmail.accountant]
\\
I am Minister James Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 25th of April, 1948, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 666 tonnes of cotton Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 31\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister James Okon
\\\\
Jane thinks that this guy is really responsible, and sends him some money.
John receives 195 Emerald Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a convoluted network of ropes, made from ebony.
John strangles Jane.
Her face turns violet.
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a ivory telescope, made in China.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her games room window.
John knows Jane's secret. What is her secret? She is a gerontosexual amorgender unicat, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a orange vinyl floor, and the walls are painted crimson.
Jane's personal serving{-}room has a marble bed, with mauve daffodil petals strewn about it.
Jane is dressed in a blonde dress made from satin.
John pays Jane 391 Emerald Bills.
John soaks her cyan furniture.
Jane bellows in depraved indulgence, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Escort, And John Is Her Customer}


The brothel has a apricot vinyl floor, and the walls are painted blue.
Jane's personal serving{-}room has a aluminium bed, with peach daffodil petals strewn about it.
Jane is dressed in a blue nightgown made from cashmere.
John pays Jane 277 Golden Quarters.
John crawls into her cream furniture.
Jane cries out in diabolical rapture, and John continues throughout the night...
\subsection{A Timeline In Which John Pillages Jane}


John breaks into the apartment with a iron lockpick, and looks around.
The apartment has a scarlet tile floor, and the walls are painted cobalt.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from plastic.
He then gags her, using a glass ring{-}gag.
John rushes her red spoon.
Jane squeals in degenerate pleasure, and John continues throughout the night...
\subsection{A Timeline In Which John Debauches Jane}


John breaks into the apartment with a iron lockpick, and looks around.
The apartment has a cobalt wood floor, and the walls are painted apricot.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a wire frame, made from ebony.
He then gags her, using a cotton spider{-}gag.
John unlocks her emerald goat.
Jane howls in diabolical indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Intimidates Jane}


John pulls out a letter, encased in a crimson envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} blueskunk946@xmail.post {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a specially modified bed, made from iridium.
John asphyxiates Jane.
Her face turns sky{-}blue.
\subsection{A Timeline In Which John Sullies Jane}


John breaks into the apartment with a ebony sledgehammer, and looks around.
The apartment has a purple tile floor, and the walls are painted pink.
John slips into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from rubber.
He then gags her, using a glass spider{-}gag.
John sniffs her azure tent.
Jane howls in impious delight, and John continues throughout the night...
\subsection{A Timeline In Which John Sells ErsatzGoods To Jane}


It is dismal and run{-}down, with a sleazy black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with technicolour stalls, with soupy smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from oak and covered with apricot silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pipe made by Disney.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 311 Bear Quarters, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Lady Of The Night, And John Is Her Customer}


The brothel has a teal carpet floor, and the walls are painted scarlet.
Jane's personal serving{-}room has a aluminium bed, with blue tulip petals strewn about it.
Jane is dressed in a pink nightgown made from lace.
John pays Jane 338 Golden Crowns.
John spreads her cream rabbit.
Jane shouts in fiendish relish, and John continues throughout the night...
\subsection{A Timeline In Which John Knocks Out Jane}


John pulls out a small cream packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than futaparin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Fizz.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly nauseous, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Alarms Jane With A Revolver}


John is sitting in the cafe.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a U{-}94 Udar.
John gesticulates at Jane with his revolver. Her face becomes pale, and John knows that she will comply with with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from osmium.
John pulls out a cyan kukri, made out of titanium.
He transfixes Jane with the kukri.
Ruby blood spews out from the wound.
\subsection{A Timeline In Which John Sells PhonyGoods To Jane}


It is dismal and dark, with a rough black market hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with highly colourful stalls, with murky smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from oak and covered with emerald denim.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigarettes made by Versace.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 361 Bear Bits, and is pleased with his gain.
\subsection{A Timeline In Which John Punctures Jane With A Blade}


John immobilizes Jane, using a specially modified bed, made from ebony.
John pulls out a apricot dirk, made out of Damascus stel.
He spears Jane with the dirk.
Carmine liquid spurts out from the wound.
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a virtual reality device, made from uranium glass.
John garrottes Jane.
Her face turns sky{-}blue.
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a rose envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} pinkbat907@bmail.adult {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Off Herself}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a currish rude{-}growing bugbear?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was flawless, Jane thinks.
In fact, the more she mulls over his argument, the more she realizes it was almost certainly precise, and resigns herself.
Jane pulls out a revolver {-} a Charter Arms Bulldog {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Coral lumps soak the pink walls, and cherry ichor pools upon the floor.
\subsection{A Timeline In Which John Laces A Drink For Jane}


John pulls out a small lilac packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than tryptopramine, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Fizz.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels fairly nauseous, but it passes.
More dangerously, however, she is rendered malleable, which is exactly as John wants her...
\subsection{A Timeline In Which John Tantalizes Jane}


The apartment has a salmon linoleum floor, and the walls are painted yellow.
The bedroom has a iridium bed, with rose daffodil petals strewn about it.
John strolls to Jane, and massages her cheek.
John smothers her purple tent.
Jane squeals in unspeakable delight, and John continues throughout the night...
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a specially modified bed, made from ebony.
John strangulates Jane.
Her face turns sky{-}blue.
\subsection{A Timeline In Which John Sells Knock{-}offGoods To Jane}


It is dilapidated and dim, with a disreputable black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with like a rainbow stalls, with smoggy smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from oak and covered with teal denim.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pen made by Disney.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 386 Wondrous Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Agonizes Jane}


John immobilizes Jane, using a hypnosis machine, made from steel.
He then gags her, using a glass ball{-}gag.
John turns on the device, and the pink suction caps work their magic upon her.
Jane screams through her gag, writhing about.
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is gloomy and disintegrating, with a seamy speakeasy hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see azure walls inside the building.
John steps out of the gloom, surprising Jane.
He pokes her with an illegally bought revolver, a Smith \& Wesson Model 500.
He commands Jane to give him his money.
Shaking with fear, she hands him her pouch.
She takes her change and escapes, thankful that she survived.
John receives 480 Adamantine Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Mugs Jane}


Jane was strolling past a dark alley.
It is dim and decrepit, with a seamy opium den hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see apricot walls inside the building.
John steps out of the murk, catching Jane off{-}guard.
He jabs her with an illegally bought revolver, a Ruger Alaskan.
He instructs Jane to give him his money.
Quaking with fear, she hands him her purse.
She takes her change and legs it, thankful that she survived.
John receives 307 Bull Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Steals From Jane}


Jane was striding past a dark alley.
It is dilapidated and shabby, with a unpleasant speakeasy hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see salmon walls inside the building.
John steps out of the umbrage, surprising Jane.
He prods her with an illegally bought revolver, a Ruger Vaquero.
He directs Jane to give him his money.
Shuddering with fear, she hands him her purse.
She takes her change and legs it, thankful that she survived.
John receives 433 Indigo Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a plastic pair of binoculars, made in Skxc8aistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her box room window.
John knows Jane's secret. What is her secret? She is a heteroflexible agenderflux kilocoyote, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Stalks Jane}


He's using a plastic pair of binoculars, made in McBekistan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her bedroom window.
John knows Jane's secret. What is her secret? She is a sapiosexual cancegender septohyena, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Metahydra is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Metahydra is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a apachehelisexual scorpiogender megatiger, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Steals From Jane}


Jane was walking past a dark alley.
It is grim and dark, with a nasty opium den hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see teal walls inside the building.
John steps out of the gloom, surprising Jane.
He prods her with an illegally bought revolver, a Charter Arms Bulldog.
He instructs Jane to give him his money.
Shaking with fear, she hands him her billfold.
She takes her change and legs it, thankful that she survived.
John receives 323 Wondrous Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Airspider is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airspider is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a menosexual anogender octosnail, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Scares Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Chiappa Rhino.
John waves at Jane with his revolver. Her face whitens, and John knows that she will go along with with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Plunders Jane}


John breaks into the apartment with a iridium lockpick, and looks around.
The apartment has a salmon concrete floor, and the walls are painted aquamarine.
John slips into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from ebony.
He then gags her, using a leather ring{-}gag.
John rushes her cobalt rabbit.
Jane cries out in blasphemous bliss, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a aquamarine tile floor, and the walls are painted mauve.
Jane's personal serving{-}room has a osmium bed, with purple iris petals strewn about it.
Jane is dressed in a blonde bikini made from cotton.
John pays Jane 465 Ivory Dollars.
John locks her aquamarine chicken.
Jane screams in godless relish, and John continues throughout the night...
\subsection{A Timeline In Which John Stalks Jane}


He's using a ebony satellite dish, made in Prussia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her library window.
John knows Jane's secret. What is her secret? She is a amorplatonic librafluid octodragon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Frightens Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Ruger Alaskan.
John waves at Jane with his revolver. Her face turns pallid, and John knows that she will relent to with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Cheats Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: James Okon[pinkferret374@kmail.com]
\\
I am Doctor James Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 23th of September, 1982, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 712 tonnes of glass Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 42\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor James Okon
\\\\
Jane thinks that this guy is really honourable, and sends him some money.
John receives 309 Golden Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Beguiles Jane}


The apartment has a aquamarine carpet floor, and the walls are painted rose.
The bedroom has a spruce bed, with yellow violet petals strewn about it.
John lazily walks to Jane, and kisses her lips.
John pushs her azure spork.
Jane cries out in impious sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Metamap is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Metamap is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a menosexual amorgender millihorse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Allures Jane}


The apartment has a apricot cement floor, and the walls are painted scarlet.
The bedroom has a steel bed, with scarlet chrysantheum petals strewn about it.
John ambles to Jane, and kisses her lips.
John grinds her lilac spoon.
Jane cries out in diabolical indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Renders Insensible Jane}


John pulls out a small cream packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than betacillin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Daiquiri.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels slightly nauseous, but it passes.
More dangerously, however, she is rendered impressionable, which is exactly as John wants her...
\subsection{A Timeline In Which John Surveils Jane}


He's using a iridium scope, made in Yugoslavia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her hall window.
John knows Jane's secret. What is her secret? She is a sapiosexual scorpiogender kilodog, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Pillages Jane}


John breaks into the apartment with a iridium hammer, and looks around.
The apartment has a mauve carpet floor, and the walls are painted rose.
John steals into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from uranium glass.
He then gags her, using a leather spider{-}gag.
John soaks her orange spork.
Jane cries out in unspeakable bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a brainwasher, made from cotton.
John pulls out a salmon butterfly knife, made out of newspaper.
He gores Jane with the butterfly knife.
Claret liquid spouts out from the wound.
\subsection{A Timeline In Which Jane Is A Lady Of The Night, And John Is Her Customer}


The brothel has a scarlet tile floor, and the walls are painted yellow.
Jane's personal serving{-}room has a rubber bed, with teal violet petals strewn about it.
Jane is dressed in a rose nightgown made from muslin.
John pays Jane 247 Ebony Marks.
John satisfies her teal goat.
Jane squeals in impious joy, and John continues throughout the night...
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a hypnosis machine, made from glass.
John strangles Jane.
Her face turns blue.
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a frame, made from osmium.
He then gags her, using a steel ring{-}gag.
John turns on the device, and the blue knives work their magic upon her.
Jane whimpers through her gag, writhing about.
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from cotton.
John pulls out a yellow dirk, made out of aluminium.
He wounds Jane with the dirk.
Claret fluid gushes out from the wound.
\subsection{A Timeline In Which John Wrings Jane}


John pulls out a letter, encased in a orange envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} cobaltskunk862@chainmail.com {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Swindles Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: James Okon[cobaltlynx537@rmail.io]
\\
I am Minister James Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 15th of April, 1980, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 10983 tonnes of hemp Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 18\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister James Okon
\\\\
Jane thinks that this guy is really incorruptible, and sends him some money.
John receives 424 Emerald Quarters, and is pleased with his gain.
\subsection{A Timeline In Which John Pollutes Jane}


John breaks into the apartment with a ceramic hacking PDA, and looks around.
The apartment has a scarlet stone floor, and the walls are painted blue.
John steals into Jane's bedroom.
John immobilizes Jane, using a wire frame, made from glass.
He then gags her, using a hemp spider{-}gag.
John tempts her purple swamp.
Jane bellows in unspeakable ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Steals From Jane}


Jane was trudging past a dark alley.
It is drab and decaying, with a corrupt opium den hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see orange walls inside the building.
John steps out of the shadows, taking Jane by surprise.
He prods her with an illegally bought revolver, a Ruger Alaskan.
He directs Jane to give him his money.
Trembling with fear, she hands him her pochette.
She takes her change and gets out, thankful that she survived.
John receives 249 Planetary Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Watches Jane}


He's using a osmium satellite dish, made in Portugal.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her bathroom window.
John knows Jane's secret. What is her secret? She is a objectumsexual mirrorgender decacheetah, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Maltreats Jane}


John immobilizes Jane, using a frame, made from rubber.
He then gags her, using a glass rag.
John turns on the device, and the lilac electrodes work their magic upon her.
Jane whimpers through her gag, trying to escape.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a beslubbering common{-}kissing scut?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was precise, Jane thinks.
In fact, the more she reviews his argument, the more she realizes it was almost certainly flawless, and resigns herself.
Jane pulls out a revolver {-} a Ruger Vaquero {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Taffy lumps douse the cream walls, and rusty blood pools upon the floor.
\subsection{A Timeline In Which John Keeps An Eye On Jane}


He's using a glass long{-}range camera, made in Italy.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her box room window.
John knows Jane's secret. What is her secret? She is a gynosexual cheiragender terarabbit, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Pressurizes Jane With A Revolver}


John is sitting in the cafe.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a U{-}94 Udar.
John gesticulates at Jane with his revolver. Her face becomes pale, and John knows that she will yield to with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Spikes A Drink For Jane}


John pulls out a small green packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than avanastatin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Martini.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels nauseous, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a droning dread{-}bolted pigeon{-}egg?
You know, Jane, maybe you should just end it all.'
Maybe his argument was right, Jane thinks.
In fact, the more she weighs up his argument, the more she realizes it was almost certainly veracious, and resigns herself.
Jane pulls out a revolver {-} a Ruger Vaquero {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink masses slosh across the orange walls, and vermilion ichor pools upon the floor.
\subsection{A Timeline In Which John Exploits Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Jamie Smith[apricotbat796@kmail.gray]
\\
I am Minister Jamie Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 12th of December, 1928, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 528 tonnes of ebony Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 27\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Smith
\\\\
Jane thinks that this guy is really incorruptible, and sends him some money.
John receives 395 Marvelous Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Steals From Jane}


Jane was walking past a dark alley.
It is dismal and dirty, with a seamy bordello hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see blonde walls inside the building.
John steps out of the gloominess, taking Jane by surprise.
He jabs her with an illegally bought revolver, a Ruger Vaquero.
He commands Jane to give him his money.
Shuddering with fear, she hands him her pocketbook.
She takes her change and slips away, thankful that she survived.
John receives 143 Marvelous Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a virtual reality device, made from ebony.
He then gags her, using a aluminium spider{-}gag.
John turns on the device, and the aquamarine suction caps work their magic upon her.
Jane howls through her gag, thrashing about.
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a hypnosis machine, made from leather.
John garrottes Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Digphoenix is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Digphoenix is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a sapiosexual chaosflux heptokangaroo, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a specially modified bed, made from leather.
John strangles Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Hypnotizes Jane}


The apartment has a cyan stone floor, and the walls are painted orange.
The bedroom has a ivory bed, with blue rose petals strewn about it.
John lazily walks to Jane, and lightly bites her cheek.
John flosses her yellow seamstress.
Jane howls in sacrilegious excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is cheerless and dull, with a rough black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with highly colourful stalls, with soupy vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from teak and covered with mauve satin.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit shoes made by Rolex.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 478 Ivory Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Demands Hush Money From Jane}


John pulls out a letter, encased in a emerald envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} orangedog252@ymail.cyan {-} he added soon...
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a osmium laser microphone, made in England.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her conservatory window.
John knows Jane's secret. What is her secret? She is a androphiliac aliusgender hectolion, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Torments Jane}


John immobilizes Jane, using a virtual reality device, made from cotton.
He then gags her, using a ebony ball{-}gag.
John turns on the device, and the mauve suction caps work their magic upon her.
Jane wails through her gag, writhing about.
\subsection{A Timeline In Which John Demands Hush Money From Jane}


John pulls out a letter, encased in a pink envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} blondefox529@amail.yellow {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Knocks Out Jane}


John pulls out a small peach packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than avanazosin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Gimlet.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very nauseous, but it passes.
More dangerously, however, she is rendered docile, which is exactly as John wants her...
\subsection{A Timeline In Which John Tortures Jane}


John immobilizes Jane, using a virtual reality device, made from iridium.
He then gags her, using a cotton ring{-}gag.
John turns on the device, and the scarlet electrodes work their magic upon her.
Jane wails through her gag, writhing about.
\subsection{A Timeline In Which John Knocks Out Jane}


John pulls out a small cyan packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than ometriptan, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Cosmopolitan.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels fairly nauseous, but it passes.
More dangerously, however, she is rendered pliable, which is exactly as John wants her...
\subsection{A Timeline In Which John Scams Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: URGENT
FROM: Jamie Bonganti[purplefox473@bmail.accountant]
\\
I am Minister Jamie Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 2th of February, 1961, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 712 tonnes of titanium Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 26\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Bonganti
\\\\
Jane thinks that this guy is really reliable, and sends him some money.
John receives 361 Bull Quarters, and is pleased with his gain.
\subsection{A Timeline In Which John Stabs Jane With A Blade}


John immobilizes Jane, using a frame, made from cotton.
John pulls out a cream dirk, made out of newspaper.
He impales Jane with the dirk.
Rusty liquid pours out from the wound.
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a mummering rump{-}fed clack{-}dish?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was correct, Jane thinks.
In fact, the more she ruminates over his argument, the more she realizes it was almost certainly veracious, and resigns herself.
Jane pulls out a revolver {-} a Ruger Alaskan {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Strawberry bits spatter the cobalt walls, and rosy ichor pools upon the floor.
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is dilapidated and disintegrating, with a unpleasant black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with murky smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from birch and covered with teal satin.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigar made by Montblanc.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 376 Indigo Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Maltreats Jane}


John breaks into the apartment with a iridium lockpick, and looks around.
The apartment has a teal concrete floor, and the walls are painted cream.
John sneaks into Jane's bedroom.
John immobilizes Jane, using a virtual reality device, made from cotton.
He then gags her, using a glass ring{-}gag.
John rubs her salmon zoo.
Jane howls in sacrilegious relish, and John continues throughout the night...
\subsection{A Timeline In Which John Allures Jane}


The apartment has a blonde cement floor, and the walls are painted lilac.
The bedroom has a titanium bed, with pink chrysantheum petals strewn about it.
John darts over to Jane, and licks her cheek.
John wraps her lilac rabbit.
Jane cries out in diabolical indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a pernicious idle{-}headed lout?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was faultless, Jane thinks.
In fact, the more she contemplates his argument, the more she realizes it was almost certainly on the nail, and resigns herself.
Jane pulls out a revolver {-} a Charter Arms Bulldog {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rouge lumps moisten the cyan walls, and carmine ichor pools upon the floor.
\subsection{A Timeline In Which John Extorts Money From Jane}


John pulls out a letter, encased in a scarlet envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} mauvelion354@chainmail.landica {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Pillages Jane}


John breaks into the apartment with a uranium glass sledgehammer, and looks around.
The apartment has a green wood floor, and the walls are painted pink.
John slips into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from uranium glass.
He then gags her, using a aluminium ball{-}gag.
John pushs her peach llama.
Jane howls in profane rapture, and John continues throughout the night...
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a specially modified bed, made from leather.
John garrottes Jane.
Her face turns cyan.
\subsection{A Timeline In Which John Kills Jane With A Blade}


John immobilizes Jane, using a brainwasher, made from leather.
John pulls out a cream knife, made out of titanium.
He perforates Jane with the knife.
Carmine ichor streams out from the wound.
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a specially modified bed, made from rubber.
John pulls out a cobalt spear, made out of chrome.
He gores Jane with the spear.
Cerise liquid pours out from the wound.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a titanium scope, made in Australia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her games room window.
John knows Jane's secret. What is her secret? She is a amorplatonic digigender kilofox, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Maltosploit is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Maltosploit is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a idemromantic burstgender bilynx, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Hypnotizes Jane}


The apartment has a yellow vinyl floor, and the walls are painted azure.
The bedroom has a osmium bed, with salmon iris petals strewn about it.
John ambles to Jane, and lightly bites her lips.
John brushes her teal swamp.
Jane squeals in degenerate delight, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Escort, And John Is Her Customer}


The brothel has a scarlet carpet floor, and the walls are painted blonde.
Jane's personal serving{-}room has a oak bed, with red daisy petals strewn about it.
Jane is dressed in a lilac negligee made from satin.
John pays Jane 489 Perfected Bits.
John tempts her crimson bomb site B.
Jane screams in degenerate indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Steals From Jane}


Jane was trudging past a dark alley.
It is derelict and crumbling, with a disreputable black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see green walls inside the building.
John steps out of the darkness, surprising Jane.
He prods her with an illegally bought revolver, a Charter Arms Bulldog.
He orders Jane to give him his money.
Shaking with fear, she hands him her pochette.
She takes her change and bolts, thankful that she survived.
John receives 163 Wondrous Sultanates, and is pleased with his gain.
\subsection{A Timeline In Which John Spies Upon Jane}


He's using a plastic pair of binoculars, made in Yugoslavia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her dining room window.
John knows Jane's secret. What is her secret? She is a bellusromantic bigenderfluid kiloleopard, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a set of straps, made from osmium.
John chokes Jane.
Her face turns magenta.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good morning' to her.
He then insults her {-} 'By God, aren't you a froward rude{-}growing clotpole?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was true, Jane thinks.
In fact, the more she contemplates his argument, the more she realizes it was almost certainly on the mark, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 340PD {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Coral masses slosh across the orange walls, and gules liquid pools upon the floor.
\subsection{A Timeline In Which John Makes Threats Against Jane With A Revolver}


John is sitting in the bookstore.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Colt Anaconda.
John waves at Jane with his revolver. Her face turns pallid, and John knows that she will relent to with his demands.
Jane is so quiet you could hear a pin drop. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persecutes Jane}


John immobilizes Jane, using a specially modified bed, made from cotton.
He then gags her, using a ivory ball{-}gag.
John turns on the device, and the teal blades work their magic upon her.
Jane moans through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Robs Jane}


Jane was walking past a dark alley.
It is dismal and disintegrating, with a nasty speakeasy hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see aquamarine walls inside the building.
John steps out of the murk, surprising Jane.
He pokes her with an illegally bought revolver, a Smith \& Wesson Model 340PD.
He commands Jane to give him his money.
Trembling with fear, she hands him her wallet.
She takes her change and makes a break for it, thankful that she survived.
John receives 496 Bear Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Demands Hush Money From Jane}


John pulls out a letter, encased in a azure envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} lilacsquirrel122@wmail.int {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Maltreats Jane}


John breaks into the apartment with a steel lockpick, and looks around.
The apartment has a mint tile floor, and the walls are painted cream.
John steals into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from ebony.
He then gags her, using a aluminium rag.
John soaks her pink seamstress.
Jane squeals in depraved joy, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Courtesan, And John Is Her Customer}


The brothel has a red concrete floor, and the walls are painted lilac.
Jane's personal serving{-}room has a oak bed, with azure hyacinth petals strewn about it.
Jane is dressed in a apricot teddy made from gauze.
John pays Jane 499 Radiant Marks.
John drills her scarlet spork.
Jane cries out in godless euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Exploits Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: important and confidential
FROM: Mike Okon[orangebat344@tmail.green]
\\
I am Minister Mike Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 21th of September, 1975, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 169 tonnes of glass Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 36\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Mike Okon
\\\\
Jane thinks that this guy is really responsible, and sends him some money.
John receives 260 Golden Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Punctures Jane With A Blade}


John immobilizes Jane, using a wire frame, made from iridium.
John pulls out a cobalt push{-}dagger, made out of titanium.
He slashes Jane with the push{-}dagger.
Rosy liquid rushes out from the wound.
\subsection{A Timeline In Which John Allures Jane}


The apartment has a blonde carpet floor, and the walls are painted teal.
The bedroom has a uranium glass bed, with rose iris petals strewn about it.
John walks to Jane, and kisses her ear.
John sniffs her azure system.
Jane cries out in godless euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Mugs Jane}


Jane was trudging past a dark alley.
It is grim and cheerless, with a disreputable speakeasy hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see red walls inside the building.
John steps out of the shadows, taking Jane by surprise.
He nudges her with an illegally bought revolver, a Ruger Alaskan.
He instructs Jane to give him his money.
Shuddering with fear, she hands him her pocketbook.
She takes her change and legs it, thankful that she survived.
John receives 174 Ebony Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Stabs Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from cotton.
John pulls out a rose sword, made out of iron.
He wounds Jane with the sword.
Cerise blood jets out from the wound.
\subsection{A Timeline In Which John Violates Jane}


John breaks into the apartment with a osmium hammer, and looks around.
The apartment has a orange concrete floor, and the walls are painted cream.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a forcefield generator, made from hemp.
He then gags her, using a plastic ball{-}gag.
John grinds her orange zoo.
Jane bellows in base pleasure, and John continues throughout the night...
\subsection{A Timeline In Which John Gores Jane With A Blade}


John immobilizes Jane, using a virtual reality device, made from hemp.
John pulls out a cyan sword, made out of titanium.
He penetrates Jane with the sword.
Maroon blood spills out from the wound.
\subsection{A Timeline In Which John Ravishes Jane}


John breaks into the apartment with a iridium lockpick, and looks around.
The apartment has a peach cement floor, and the walls are painted salmon.
John prowls into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from aluminium.
He then gags her, using a glass ball{-}gag.
John sniffs her yellow furniture.
Jane screams in godless joy, and John continues throughout the night...
\subsection{A Timeline In Which John Dupes Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: James Bankole[cobaltsquirrel230@smail.pizza]
\\
I am Minister James Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 22th of May, 1965, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 10983 tonnes of glass Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 40\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister James Bankole
\\\\
Jane thinks that this guy is really incorruptible, and sends him some money.
John receives 307 Marvelous Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Robs Jane}


Jane was striding past a dark alley.
It is drab and dull, with a sordid bordello hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see purple walls inside the building.
John steps out of the murk, catching Jane off{-}guard.
He prods her with an illegally bought revolver, a Taurus Judge.
He orders Jane to give him his money.
Swaying with fear, she hands him her wallet.
She takes her change and steals away, thankful that she survived.
John receives 423 Prismatic Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a iridium spyglass, made in Germany.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her greenhouse window.
John knows Jane's secret. What is her secret? She is a apothi mirrorgender heptocoyote, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Rips Off Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: James Smith[creamhyena87@ymail.mil]
\\
I am Doctor James Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 1th of October, 1971, my client and his wife and their only daughter were in a car crash on the main road from Lagos to Kaduna (they died).
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 263 tonnes of steel Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 29\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor James Smith
\\\\
Jane thinks that this guy is really reliable, and sends him some money.
John receives 422 Emerald Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a specially modified bed, made from titanium.
John chokes Jane.
Her face turns cyan.
\subsection{A Timeline In Which John Cheats Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: important and confidential
FROM: Jamie Bankole[redsquirrel90@cmail.net]
\\
I am Minister Jamie Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 29th of May, 1991, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1579 tonnes of steel Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 30\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Bankole
\\\\
Jane thinks that this guy is really virtuous, and sends him some money.
John receives 224 Elevated Ducats, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a teal tile floor, and the walls are painted cream.
Jane's personal serving{-}room has a leather bed, with cream hyacinth petals strewn about it.
Jane is dressed in a blonde nightgown made from gauze.
John pays Jane 432 Indigo Marks.
John soaks her emerald goat.
Jane squeals in godless joy, and John continues throughout the night...
\subsection{A Timeline In Which John Intimidates Jane}


John pulls out a letter, encased in a emerald envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} mauvebull693@fmail.pizza {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a convoluted network of ropes, made from cotton.
John pulls out a rose dirk, made out of titanium.
He slashes Jane with the dirk.
Claret fluid surges out from the wound.
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small green packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than clofil, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Martini.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly dizzy, but it passes.
More dangerously, however, she is rendered susceptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a loggerheaded elf{-}skinned dewberry?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was spot on, Jane thinks.
In fact, the more she ruminates over his argument, the more she realizes it was almost certainly true, and resigns herself.
Jane pulls out a revolver {-} a Ruger Alaskan {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Coral masses drench the blue walls, and cherry liquid pools upon the floor.
\subsection{A Timeline In Which John Kills Jane With A Blade}


John immobilizes Jane, using a hypnosis machine, made from aluminium.
John pulls out a pink butterfly knife, made out of wood.
He gores Jane with the butterfly knife.
Carmine fluid spews out from the wound.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a beslubbering dread{-}bolted hedge{-}pig?
You know, Jane, maybe you should just end it all.'
Maybe his argument was true, Jane thinks.
In fact, the more she reflects upon his argument, the more she realizes it was almost certainly precise, and resigns herself.
Jane pulls out a revolver {-} a Ruger Alaskan {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Pink masses spatter across the mauve walls, and scarlet blood pools upon the floor.
\subsection{A Timeline In Which John Besmirches Jane}


John breaks into the apartment with a carbon nanotube hammer, and looks around.
The apartment has a scarlet concrete floor, and the walls are painted pink.
John steals into Jane's bedroom.
John immobilizes Jane, using a brainwasher, made from osmium.
He then gags her, using a cotton rag.
John soaks her pink spoon.
Jane screams in impious indulgence, and John continues throughout the night...
\subsection{A Timeline In Which John Threatens Jane With A Revolver}


John is sitting in the pub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a MP{-}412 REX.
John gesticulates at Jane with his revolver. Her face loses colour, and John knows that she will comply with with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Wirebull is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Wirebull is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a amicussexual zodiacgender quadrarabbit, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good evening' to her.
He then insults her {-} 'By God, aren't you a saucy spur{-}galled vassal?
You know, Jane, maybe you should just die by your own hand.'
Maybe his argument was precise, Jane thinks.
In fact, the more she weighs up his argument, the more she realizes it was almost certainly precise, and resigns herself.
Jane pulls out a revolver {-} a Taurus Judge {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Strawberry bits bespatter the red walls, and flaming ichor pools upon the floor.
\subsection{A Timeline In Which John Defrauds Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: TREAT AS URGENT
FROM: Jamie Bonganti[cyanlynx106@imail.black]
\\
I am Doctor Jamie Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 12th of September, 1936, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1598 tonnes of titanium Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 48\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Jamie Bonganti
\\\\
Jane thinks that this guy is really upright, and sends him some money.
John receives 240 Imperial Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Stains Jane}


John breaks into the apartment with a plastic hammer, and looks around.
The apartment has a peach cement floor, and the walls are painted rose.
John prowls into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from iridium.
He then gags her, using a steel ring{-}gag.
John wraps her apricot chicken.
Jane shouts in base rapture, and John continues throughout the night...
\subsection{A Timeline In Which John Sells Knock{-}offGoods To Jane}


It is run{-}down and broken{-}down, with a disreputable black market hidden behind a secretive door.
Smoke oozes out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with many{-}hued stalls, with heavy haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from mahogany and covered with yellow linen.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pipe made by Gucci.
Jane buys the item, and navigates around the black market until she finds the exit, leaving.
John receives 452 Golden Notes, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good evening' to her.
He then insults her {-} 'By God, aren't you a craven fen{-}sucked measle?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was veracious, Jane thinks.
In fact, the more she contemplates his argument, the more she realizes it was almost certainly on the money, and resigns herself.
Jane pulls out a revolver {-} a Manurhin MR 73 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink gobs moisten the peach walls, and vermilion liquid pools upon the floor.
\subsection{A Timeline In Which John Stalks Jane Using The Internet}


Datawasp is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Datawasp is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a gynosexual affectugender kilocat, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Extorts Money From Jane}


John pulls out a letter, encased in a lilac envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} purplesquirrel894@bmail.red {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Punctures Jane With A Blade}


John immobilizes Jane, using a frame, made from glass.
John pulls out a rose sword, made out of titanium.
He punctures Jane with the sword.
Cerise ichor spills out from the wound.
\subsection{A Timeline In Which John Bullies Jane With A Revolver}


John is sitting in the bookstore.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a MP{-}412 REX.
John waves at Jane with his revolver. Her face whitens, and John knows that she will yield to with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Milks Jane}


John pulls out a letter, encased in a mauve envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} mauvecat208@omail.io {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Pillages Jane}


John breaks into the apartment with a plastic hammer, and looks around.
The apartment has a blue stone floor, and the walls are painted aquamarine.
John pads into Jane's bedroom.
John immobilizes Jane, using a frame, made from uranium glass.
He then gags her, using a hemp rag.
John smothers her scarlet tent.
Jane screams in profane joy, and John continues throughout the night...
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a forcefield generator, made from uranium glass.
John strangles Jane.
Her face turns violet.
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a droning clapper{-}clawed jolt{-}head?
You know, Jane, maybe you should just end it all.'
Maybe his argument was precise, Jane thinks.
In fact, the more she reflects upon his argument, the more she realizes it was almost certainly on the money, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 340PD {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Pale pink chunks spatter the salmon walls, and red fluid pools upon the floor.
\subsection{A Timeline In Which John Narcotizes Jane}


John pulls out a small yellow packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than acetazosin, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Mai Tai.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly nauseous, but it passes.
More dangerously, however, she is rendered susceptible, which is exactly as John wants her...
\subsection{A Timeline In Which John Allures Jane}


The apartment has a aquamarine linoleum floor, and the walls are painted lilac.
The bedroom has a hemp bed, with rose iris petals strewn about it.
John wanders to Jane, and massages her ear.
John drills her green furniture.
Jane squeals in degenerate excitement, and John continues throughout the night...
\subsection{A Timeline In Which Jane Is A Call Girl, And John Is Her Customer}


The brothel has a mint carpet floor, and the walls are painted red.
Jane's personal serving{-}room has a steel bed, with red tulip petals strewn about it.
Jane is dressed in a green negligee made from cotton.
John pays Jane 160 Imperial Ducats.
John milks her purple goat.
Jane bellows in impious excitement, and John continues throughout the night...
\subsection{A Timeline In Which John Frightens Jane With A Revolver}


John is sitting in the pub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Ruger Vaquero.
John gestures at Jane with his revolver. Her face becomes pale, and John knows that she will go along with with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Enchants Jane}


The apartment has a blonde concrete floor, and the walls are painted teal.
The bedroom has a ivory bed, with crimson iris petals strewn about it.
John saunters to Jane, and licks her ear.
John tempts her purple seamstress.
Jane shouts in blasphemous delight, and John continues throughout the night...
\subsection{A Timeline In Which John Watches Jane}


He's using a steel spyglass, made in Russia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her library window.
John knows Jane's secret. What is her secret? She is a quoiromantic ambonec centihorse, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Adulterates Jane}


John breaks into the apartment with a titanium hacking PDA, and looks around.
The apartment has a red tile floor, and the walls are painted lilac.
John steals into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from uranium glass.
He then gags her, using a leather ring{-}gag.
John wraps her emerald system.
Jane shouts in fiendish gratification, and John continues throughout the night...
\subsection{A Timeline In Which John Vitiates Jane}


John breaks into the apartment with a uranium glass crowbar, and looks around.
The apartment has a cobalt stone floor, and the walls are painted blonde.
John pads into Jane's bedroom.
John immobilizes Jane, using a virtual reality device, made from aluminium.
He then gags her, using a leather ring{-}gag.
John flosses her orange boat.
Jane squeals in profane sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Demands Hush Money From Jane}


John pulls out a letter, encased in a cream envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} orangebear287@ymail.com {-} he added soon...
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is shabby and ruinous, with a sordid black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with like a rainbow stalls, with murky smoke swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from maple and covered with lilac linen.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit snuff tobacco bottle made by Mercedes{-}Benz.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 234 Golden Marks, and is pleased with his gain.
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a hypnosis machine, made from steel.
John chokes Jane.
Her face turns cyan.
\subsection{A Timeline In Which John Punctures Jane With A Blade}


John immobilizes Jane, using a brainwasher, made from glass.
John pulls out a aquamarine spear, made out of iron.
He gores Jane with the spear.
Flaming blood surges out from the wound.
\subsection{A Timeline In Which John Enchants Jane}


The apartment has a emerald cement floor, and the walls are painted scarlet.
The bedroom has a plastic bed, with aquamarine iris petals strewn about it.
John walks to Jane, and massages her earlobe.
John unlocks her scarlet swamp.
Jane squeals in godless bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Beguiles Jane}


The apartment has a purple tile floor, and the walls are painted teal.
The bedroom has a glass bed, with blonde chrysantheum petals strewn about it.
John strolls to Jane, and sucks upon her cheek.
John locks her mauve furniture.
Jane shouts in diabolical joy, and John continues throughout the night...
\subsection{A Timeline In Which John Rips Off Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: James Bonganti[peachrat558@pmail.yellow]
\\
I am Barrister James Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 13th of July, 1918, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1598 tonnes of iridium Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 47\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister James Bonganti
\\\\
Jane thinks that this guy is really honourable, and sends him some money.
John receives 152 Wondrous Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Makes Enquiries About Jane Using The Internet}


Digwasp is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Digwasp is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a objectumsexual anogender decabat, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Wheedles Jane}


The apartment has a cream carpet floor, and the walls are painted peach.
The bedroom has a steel bed, with emerald chrysantheum petals strewn about it.
John ambles to Jane, and sucks upon her lips.
John soaks her aquamarine furniture.
Jane cries out in base sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Intimidates Jane}


John pulls out a letter, encased in a orange envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} scarletgryphon574@zmail.post {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a cream vinyl floor, and the walls are painted apricot.
Jane's personal serving{-}room has a acacia bed, with green hyacinth petals strewn about it.
Jane is dressed in a yellow dress made from flax.
John pays Jane 425 Indigo Guilders.
John grinds her blue zoo.
Jane howls in diabolical sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Blackmails Jane}


John pulls out a letter, encased in a purple envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} lilaccheetah226@bmail.net {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Allures Jane}


The apartment has a yellow wood floor, and the walls are painted salmon.
The bedroom has a ebony bed, with pink iris petals strewn about it.
John darts over to Jane, and sucks upon her neck.
John wraps her rose spoon.
Jane cries out in fiendish bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a hypnosis machine, made from rubber.
John strangles Jane.
Her face turns blue.
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a brainwasher, made from ebony.
He then gags her, using a rubber ball{-}gag.
John turns on the device, and the peach spikes work their magic upon her.
Jane shrieks through her gag, trying to escape.
\subsection{A Timeline In Which John Stains Jane}


John breaks into the apartment with a ceramic lockpick, and looks around.
The apartment has a cream carpet floor, and the walls are painted azure.
John slips into Jane's bedroom.
John immobilizes Jane, using a set of straps, made from iridium.
He then gags her, using a ebony rag.
John grinds her emerald boat.
Jane cries out in dark ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Watches Jane}


He's using a glass scope, made in Austria{-}Hungary.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her box room window.
John knows Jane's secret. What is her secret? She is a kalossexual ambigender hexaraccoon, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Steals From Jane}


Jane was striding past a dark alley.
It is grimy and decrepit, with a sleazy black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see lilac walls inside the building.
John steps out of the gloominess, surprising Jane.
He prods her with an illegally bought revolver, a Taurus Judge.
He instructs Jane to give him his money.
Shuddering with fear, she hands him her purse.
She takes her change and flees, thankful that she survived.
John receives 382 Ebony Bits, and is pleased with his gain.
\subsection{A Timeline In Which John Scares Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Chiappa Rhino.
John gestures at Jane with his revolver. Her face becomes pale, and John knows that she will comply with with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Chokes Jane}


John immobilizes Jane, using a frame, made from steel.
John strangles Jane.
Her face turns cyan.
\subsection{A Timeline In Which John Vitiates Jane}


John breaks into the apartment with a iron crowbar, and looks around.
The apartment has a scarlet tile floor, and the walls are painted pink.
John prowls into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from uranium glass.
He then gags her, using a glass ball{-}gag.
John drills her peach tent.
Jane shouts in profane pleasure, and John continues throughout the night...
\subsection{A Timeline In Which John Cheats Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: important and confidential
FROM: Jamie Bonganti[tealrabbit758@bmail.io]
\\
I am Minister Jamie Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 6th of January, 1944, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 712 tonnes of aluminium Left behind by my client before it get confiscated or declared unservicable by Plunder \& Flee Incorporated, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Plunder \& Flee Incorporated have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 46\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Bonganti
\\\\
Jane thinks that this guy is really worthy of her trust, and sends him some money.
John receives 470 Adamantine Pieces, and is pleased with his gain.
\subsection{A Timeline In Which John Frightens Jane With A Revolver}


John is sitting in the pub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Chiappa Rhino.
John gesticulates at Jane with his revolver. Her face becomes pale, and John knows that she will comply with with his demands.
Jane is silent. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a osmium long{-}range camera, made in Japan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her box room window.
John knows Jane's secret. What is her secret? She is a gynephiliac aliusgender heptolion, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Distresses Jane}


John immobilizes Jane, using a hypnosis machine, made from leather.
He then gags her, using a hemp ball{-}gag.
John turns on the device, and the cream constricting straps work their magic upon her.
Jane moans through her gag, trying to wriggle out of the device.
\subsection{A Timeline In Which John Dupes Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Mike Smith[peachleopard173@kmail.blue]
\\
I am Doctor Mike Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 20th of December, 1956, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1350 tonnes of glass Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 32\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Mike Smith
\\\\
Jane thinks that this guy is really incorruptible, and sends him some money.
John receives 292 Marvelous Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Swindles Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Mike Bankole[orangesquirrel23@tmail.criminal]
\\
I am Minister Mike Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 29th of March, 1961, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 528 tonnes of ivory Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 22\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Mike Bankole
\\\\
Jane thinks that this guy is really worthy of her trust, and sends him some money.
John receives 356 Perfected Ducats, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a apricot tile floor, and the walls are painted blonde.
Jane's personal serving{-}room has a leather bed, with aquamarine iris petals strewn about it.
Jane is dressed in a emerald babydoll made from cotton.
John pays Jane 285 Elevated Pieces.
John tempts her salmon boat.
Jane cries out in godless ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a hypnosis machine, made from cotton.
John asphyxiates Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Pierces Jane With A Blade}


John immobilizes Jane, using a virtual reality device, made from ebony.
John pulls out a green sword, made out of ivory.
He pierces Jane with the sword.
Red ichor streams out from the wound.
\subsection{A Timeline In Which John Exploits Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Jamie Okon[purplecheetah971@fmail.pizza]
\\
I am Barrister Jamie Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 17th of April, 1948, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 253 tonnes of cotton Left behind by my client before it get confiscated or declared unservicable by Intercontinental Bank PLC, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Intercontinental Bank PLC have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 49\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Jamie Okon
\\\\
Jane thinks that this guy is really ethical, and sends him some money.
John receives 232 Bear Ducats, and is pleased with his gain.
\subsection{A Timeline In Which John Sells DummyGoods To Jane}


It is dismal and sombre, with a seamy black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with psychedelic stalls, with soupy haze swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from rosewood and covered with azure denim.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigar made by Montblanc.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 321 Elevated Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Garrottes Jane}


John immobilizes Jane, using a forcefield generator, made from titanium.
John throttles Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Makes Threats Against Jane With A Revolver}


John is sitting in the nightclub.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Charter Arms Bulldog.
John gesticulates at Jane with his revolver. Her face becomes pale, and John knows that she will capitulate to with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Mugs Jane}


Jane was strolling past a dark alley.
It is crumbling and shabby, with a unpleasant black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see pink walls inside the building.
John steps out of the shade, surprising Jane.
He prods her with an illegally bought revolver, a Colt Anaconda.
He directs Jane to give him his money.
Shuddering with fear, she hands him her billfold.
She takes her change and gets away, thankful that she survived.
John receives 341 Golden Dollars, and is pleased with his gain.
\subsection{A Timeline In Which John Persuades Jane To Commit Suicide}


John walks into Jane's apartment, and says 'Good morning' to her.
He then insults her {-} 'By God, aren't you a saucy fool{-}born pigeon{-}egg?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was on the mark, Jane thinks.
In fact, the more she assesses his argument, the more she realizes it was almost certainly unerring, and resigns herself.
Jane pulls out a revolver {-} a Smith \& Wesson Model 500 {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Taffy gobs spatter across the azure walls, and claret liquid pools upon the floor.
\subsection{A Timeline In Which John Bewitches Jane}


The apartment has a purple cement floor, and the walls are painted blue.
The bedroom has a acacia bed, with mauve violet petals strewn about it.
John drifts to Jane, and licks her neck.
John crawls into her crimson zoo.
Jane bellows in blasphemous euphoria, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a queasy malmsey{-}nosed lout?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was right, Jane thinks.
In fact, the more she assesses his argument, the more she realizes it was almost certainly correct, and resigns herself.
Jane pulls out a revolver {-} a Ruger Vaquero {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rosy lumps spatter the lilac walls, and flaming liquid pools upon the floor.
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good pre{-}evening' to her.
He then insults her {-} 'By God, aren't you a goatish clapper{-}clawed lout?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was right, Jane thinks.
In fact, the more she reflects upon his argument, the more she realizes it was almost certainly veracious, and resigns herself.
Jane pulls out a revolver {-} a OTs{-}20 Gnom {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink lumps spray the peach walls, and vermilion blood pools upon the floor.
\subsection{A Timeline In Which John Scams Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: URGENT
FROM: James Smith[peachrat14@chainmail.int]
\\
I am Minister James Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 23th of October, 1932, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 169 tonnes of plastic Left behind by my client before it get confiscated or declared unservicable by Disney Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Disney Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 44\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister James Smith
\\\\
Jane thinks that this guy is really reliable, and sends him some money.
John receives 479 Indigo Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Laces A Drink For Jane}


John pulls out a small crimson packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than acetalone, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Defiles Jane}


John breaks into the apartment with a iridium hammer, and looks around.
The apartment has a blonde concrete floor, and the walls are painted lilac.
John steals into Jane's bedroom.
John immobilizes Jane, using a specially modified bed, made from hemp.
He then gags her, using a hemp ring{-}gag.
John rubs her yellow tent.
Jane howls in wicked ecstasy, and John continues throughout the night...
\subsection{A Timeline In Which John Sells PiratedGoods To Jane}


It is broken{-}down and gloomy, with a seamy black market hidden behind a secretive door.
Smoke leaks out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with varicoloured stalls, with heavy smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from walnut and covered with scarlet wool.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pen made by Disney.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 154 Prismatic Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small scarlet packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than linaglitazone, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Daiquiri.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very nauseous, but it passes.
More dangerously, however, she is rendered persuadable, which is exactly as John wants her...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Hello' to her.
He then insults her {-} 'By God, aren't you a gleeking rude{-}growing ratsbane?
You know, Jane, maybe you should just kill yourself.'
Maybe his argument was on the money, Jane thinks.
In fact, the more she appraises his argument, the more she realizes it was almost certainly veracious, and resigns herself.
Jane pulls out a revolver {-} a Ruger Alaskan {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Bubblegum gobs spray the aquamarine walls, and vermilion liquid pools upon the floor.
\subsection{A Timeline In Which John Bleeds Jane}


John pulls out a letter, encased in a crimson envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} scarletbat655@omail.academy {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a virtual reality device, made from glass.
John throttles Jane.
Her face turns magenta.
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a frothy weatherbitten baggage?
You know, Jane, maybe you should just take your own life.'
Maybe his argument was veracious, Jane thinks.
In fact, the more she thinks about his argument, the more she realizes it was almost certainly right, and resigns herself.
Jane pulls out a revolver {-} a U{-}94 Udar {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Strawberry masses spatter the cobalt walls, and flaming ichor pools upon the floor.
\subsection{A Timeline In Which John Robs Jane}


Jane was striding past a dark alley.
It is decrepit and dilapidated, with a corrupt opium den hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see crimson walls inside the building.
John steps out of the murk, surprising Jane.
He pokes her with an illegally bought revolver, a MP{-}412 REX.
He directs Jane to give him his money.
Shaking with fear, she hands him her pouch.
She takes her change and runs for it, thankful that she survived.
John receives 258 Radiant Bits, and is pleased with his gain.
\subsection{A Timeline In Which John Alarms Jane With A Revolver}


John is sitting in the restaurant.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a MP{-}412 REX.
John gestures at Jane with his revolver. Her face loses colour, and John knows that she will go along with with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a craven spur{-}galled knave?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was on the mark, Jane thinks.
In fact, the more she mulls over his argument, the more she realizes it was almost certainly on the mark, and resigns herself.
Jane pulls out a revolver {-} a OTs{-}20 Gnom {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Salmon chunks douse the emerald walls, and gules liquid pools upon the floor.
\subsection{A Timeline In Which John Sells ShamGoods To Jane}


It is disintegrating and grimy, with a unpleasant black market hidden behind a secretive door.
Smoke emanates out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with highly colourful stalls, with opaque smog swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from hickory and covered with cyan polyester.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit pen made by Chanel.
Jane procures the item, and navigates around the black market until she finds the exit, leaving.
John receives 441 Marvelous Crowns, and is pleased with his gain.
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small cobalt packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than saxasetron, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Martini.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels mildly nauseous, but it passes.
More dangerously, however, she is rendered amenable, which is exactly as John wants her...
\subsection{A Timeline In Which John Extorts Money From Jane}


John pulls out a letter, encased in a mint envelope. Inside, he knows, is information known only to him and his victim. And that information will grant him power.
John sends off the letter, express post. He knows she will reply to the email address {-} lilachyena203@imail.orange {-} he added soon...
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a currish common{-}kissing clack{-}dish?
You know, Jane, maybe you should just off yourself.'
Maybe his argument was on the money, Jane thinks.
In fact, the more she ruminates over his argument, the more she realizes it was almost certainly faultless, and resigns herself.
Jane pulls out a revolver {-} a Colt Anaconda {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Rouge lumps slosh across the pink walls, and carmine liquid pools upon the floor.
\subsection{A Timeline In Which John Sells FakeGoods To Jane}


It is derelict and ruinous, with a sleazy black market hidden behind a secretive door.
Smoke exudes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with prismatic stalls, with smoggy vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from birch and covered with yellow silk.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit purse made by Versace.
Jane purchases the item, and navigates around the black market until she finds the exit, leaving.
John receives 390 Bear Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Strangulates Jane}


John immobilizes Jane, using a wire frame, made from plastic.
John throttles Jane.
Her face turns magenta.
\subsection{A Timeline In Which John Bullies Jane With A Revolver}


John is sitting in the library.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Taurus Judge.
John gestures at Jane with his revolver. Her face pales, and John knows that she will give in to with his demands.
Jane is completely quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Terrorizes Jane With A Revolver}


John is sitting in the cafe.
He sees a victim {-} Jane {-} someone he can threaten. He pulls out his gun, a revolver.
But not just any revolver, but a Charter Arms Bulldog.
John motions at Jane with his revolver. Her face whitens, and John knows that she will go along with with his demands.
Jane is quiet. She will do anything to remove the present danger. And so she complies with John's demands...
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a virtual reality device, made from ivory.
John strangulates Jane.
Her face turns cyan.
\subsection{A Timeline In Which John Laces A Drink For Jane}


John pulls out a small blonde packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than amphetocycline, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Martini.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels very dizzy, but it passes.
More dangerously, however, she is rendered receptive, which is exactly as John wants her...
\subsection{A Timeline In Which John Torments Jane}


John immobilizes Jane, using a hypnosis machine, made from iridium.
He then gags her, using a osmium rag.
John turns on the device, and the cyan constricting straps work their magic upon her.
Jane whines through her gag, squirming.
\subsection{A Timeline In Which John Exploits Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Ken Bonganti[lilacpanther747@pmail.academy]
\\
I am Doctor Ken Bonganti.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 26th of September, 1996, my client and his wife and their only daughter were killed by Prince Yomi Johnson when the Ecomog soldiers came in.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1350 tonnes of hemp Left behind by my client before it get confiscated or declared unservicable by Plunder \& Flee Incorporated, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Plunder \& Flee Incorporated have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 33\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Ken Bonganti
\\\\
Jane thinks that this guy is really worthy of her trust, and sends him some money.
John receives 307 Elevated Bits, and is pleased with his gain.
\subsection{A Timeline In Which John Engages In Espionage Upon Jane}


He's using a ebony camera, made in China.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her kitchen window.
John knows Jane's secret. What is her secret? She is a nocismasexual anogender unifox, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Titillates Jane}


The apartment has a peach tile floor, and the walls are painted blonde.
The bedroom has a rubber bed, with teal rose petals strewn about it.
John lazily walks to Jane, and lightly bites her cheek.
John rubs her teal system.
Jane cries out in fiendish bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Persuades Jane To Commit Seppuku}


John walks into Jane's apartment, and says 'Good pre{-}noon' to her.
He then insults her {-} 'By God, aren't you a reeky earth{-}vexing scut?
You know, Jane, maybe you should just commit suicide.'
Maybe his argument was on the money, Jane thinks.
In fact, the more she reflects upon his argument, the more she realizes it was almost certainly spot on, and resigns herself.
Jane pulls out a revolver {-} a OTs{-}20 Gnom {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Shell{-}pink bits douse the lilac walls, and maroon blood pools upon the floor.
\subsection{A Timeline In Which John Stains Jane}


John breaks into the apartment with a steel lockpick, and looks around.
The apartment has a blonde wood floor, and the walls are painted apricot.
John slips into Jane's bedroom.
John immobilizes Jane, using a wire frame, made from ebony.
He then gags her, using a uranium glass rag.
John wraps her scarlet furniture.
Jane cries out in impious relish, and John continues throughout the night...
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Airwolf is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airwolf is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a culparomantic aesthetgender megaleopard, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which Jane Is A Demimondaine, And John Is Her Customer}


The brothel has a mint linoleum floor, and the walls are painted cobalt.
Jane's personal serving{-}room has a ebony bed, with scarlet tulip petals strewn about it.
Jane is dressed in a purple teddy made from lace.
John pays Jane 233 Elevated Notes.
John flosses her peach goat.
Jane screams in atrocious delight, and John continues throughout the night...
\subsection{A Timeline In Which John Surveils Jane}


He's using a ebony long{-}range camera, made in Russia.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her conservatory window.
John knows Jane's secret. What is her secret? She is a heteroflexible aethergender millicheetah, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Persuades Jane To Kill Herself}


John walks into Jane's apartment, and says 'Good afternoon' to her.
He then insults her {-} 'By God, aren't you a weedy malmsey{-}nosed lout?
You know, Jane, maybe you should just end it all.'
Maybe his argument was on the right track, Jane thinks.
In fact, the more she appraises his argument, the more she realizes it was almost certainly unerring, and resigns herself.
Jane pulls out a revolver {-} a OTs{-}20 Gnom {-} and puts it against her head.
She squeezes the trigger, until BLAM!
Bubblegum masses slosh across the apricot walls, and cherry blood pools upon the floor.
\subsection{A Timeline In Which John Analyzes Jane Using The Internet}


Cybersploit is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Cybersploit is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a autosexual earthgender millilion, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a brainwasher, made from titanium.
John pulls out a blonde knife, made out of ivory.
He gashes Jane with the knife.
Red fluid gushes out from the wound.
\subsection{A Timeline In Which Jane Is A 'Companion', And John Is Her Customer}


The brothel has a mauve tile floor, and the walls are painted salmon.
Jane's personal serving{-}room has a acacia bed, with yellow tulip petals strewn about it.
Jane is dressed in a purple bikini made from cashmere.
John pays Jane 139 Emerald Hawks.
John drills her blue Disney merchandise.
Jane squeals in wicked relish, and John continues throughout the night...
\subsection{A Timeline In Which John Scourges Jane}


John immobilizes Jane, using a forcefield generator, made from ebony.
He then gags her, using a aluminium ring{-}gag.
John turns on the device, and the purple suction caps work their magic upon her.
Jane whines through her gag, trying to escape.
\subsection{A Timeline In Which John Investigates Jane Using The Internet}


Airmap is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Airmap is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a culparomantic fluidflux bisnail, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Besmirches Jane}


John breaks into the apartment with a iron sledgehammer, and looks around.
The apartment has a crimson linoleum floor, and the walls are painted crimson.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from ivory.
He then gags her, using a rubber rag.
John tempts her azure spoon.
Jane squeals in diabolical rapture, and John continues throughout the night...
\subsection{A Timeline In Which John Studies Jane Using The Internet}


Datasploit is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Datasploit is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a gerontosexual absorgender centideer, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Strangles Jane}


John immobilizes Jane, using a brainwasher, made from hemp.
John chokes Jane.
Her face turns azure.
\subsection{A Timeline In Which John Reconnoitres Jane}


He's using a osmium pair of binoculars, made in Japan.
John takes out his equipment, and points it in the direction of Jane's house. He pinpoints onto her attic window.
John knows Jane's secret. What is her secret? She is a pomosexual fluidflux septoeagle, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Defrauds Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Jamie Bankole[emeraldhorse818@bmail.apartments]
\\
I am Minister Jamie Bankole.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 30th of May, 1939, my client and his wife and their only daughter were involved in a plane crash on their way home from their holidays and were among the 111 people confirmed dead.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 169 tonnes of uranium glass Left behind by my client before it get confiscated or declared unservicable by Santi Manilo Bank, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Santi Manilo Bank have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 17\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Minister Jamie Bankole
\\\\
Jane thinks that this guy is really incorruptible, and sends him some money.
John receives 160 Prismatic Hawks, and is pleased with his gain.
\subsection{A Timeline In Which John Researchs Jane Using The Internet}


Netsploit is John's tool of choice. Able to traverse the deep{-}web and access information behind almost any barrier, Netsploit is John's personally{-}coded tool for blackmail discovery.
And finally!
John knows Jane's secret. What is her secret? She is a culparomantic alexigender hexarat, and she will do anything to ensure nobody knows.
\subsection{A Timeline In Which John Fleeces Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: James Okon[orangecoyote21@smail.whisky]
\\
I am Barrister James Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 31th of June, 1988, my client and his wife and their only daughter were kidnapped and taken away by unidentified gunmen from their home in Kaduna.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 169 tonnes of aluminium Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 16\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister James Okon
\\\\
Jane thinks that this guy is really upright, and sends him some money.
John receives 199 Wondrous Nickels, and is pleased with his gain.
\subsection{A Timeline In Which John Sells Knock{-}offGoods To Jane}


It is dirty and ruinous, with a corrupt black market hidden behind a secretive door.
Smoke issues out out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with technicolour stalls, with murky vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from pine and covered with green double gauze.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit cigarettes made by Disney.
Jane acquires the item, and navigates around the black market until she finds the exit, leaving.
John receives 363 Bear Guilders, and is pleased with his gain.
\subsection{A Timeline In Which John Dupes Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: dearest friend
FROM: Jamie Smith[blueskunk645@dmail.probablyillegal]
\\
I am Barrister Jamie Smith.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 7th of March, 1949, my client and his wife and their only daughter were in a car crash on the main road from Lagos to Kaduna (they died).
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 263 tonnes of hemp Left behind by my client before it get confiscated or declared unservicable by United Bank of Trust, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
United Bank of Trust have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 18\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Barrister Jamie Smith
\\\\
Jane thinks that this guy is really above suspicion, and sends him some money.
John receives 248 Marvelous Bills, and is pleased with his gain.
\subsection{A Timeline In Which John Stabs Jane With A Blade}


John immobilizes Jane, using a specially modified bed, made from iridium.
John pulls out a mint dirk, made out of steel.
He stabs Jane with the dirk.
Maroon ichor surges out from the wound.
\subsection{A Timeline In Which John Sells CounterfeitGoods To Jane}


It is dim and shabby, with a seamy black market hidden behind a secretive door.
Smoke escapes out of a crack in the door, and it is possible to see light emanating from inside the building.
Jane enters the black market through the wooden door.
Inside, it is filled with like a rainbow stalls, with heavy vapour swirling about in the air.
Jane wanders around the black market, until she comes upon a stall, made from birch and covered with teal polyester.
John (the merchant of this particular stall) shows her exactly what she's looking for {-} a counterfeit purse made by Prada.
Jane obtains the item, and navigates around the black market until she finds the exit, leaving.
John receives 475 Golden Crowns, and is pleased with his gain.
\subsection{A Timeline In Which John Suffocates Jane}


John immobilizes Jane, using a specially modified bed, made from iridium.
John garrottes Jane.
Her face turns lilac.
\subsection{A Timeline In Which John Harrows Jane}


John immobilizes Jane, using a forcefield generator, made from ebony.
He then gags her, using a glass ball{-}gag.
John turns on the device, and the yellow electrodes work their magic upon her.
Jane wails through her gag, squirming.
\subsection{A Timeline In Which John Pillages Jane}


John breaks into the apartment with a uranium glass hacking PDA, and looks around.
The apartment has a cyan tile floor, and the walls are painted scarlet.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a hypnosis machine, made from osmium.
He then gags her, using a cotton ball{-}gag.
John grinds her crimson chicken.
Jane squeals in atrocious sybaritism, and John continues throughout the night...
\subsection{A Timeline In Which John Ravishes Jane}


John breaks into the apartment with a plastic hammer, and looks around.
The apartment has a cyan concrete floor, and the walls are painted red.
John tiptoes into Jane's bedroom.
John immobilizes Jane, using a convoluted network of ropes, made from ivory.
He then gags her, using a hemp ring{-}gag.
John tempts her cobalt tent.
Jane bellows in profane relish, and John continues throughout the night...
\subsection{A Timeline In Which John Jabs Jane With A Blade}


John immobilizes Jane, using a virtual reality device, made from leather.
John pulls out a cyan dirk, made out of wood.
He wounds Jane with the dirk.
Claret fluid cascades out from the wound.
\subsection{A Timeline In Which John Rips Off Jane}


John had a plan to make some money {-} illegal money, but money nonetheless.
He sends an email using an illegal email address to a victim, hoping she will take the bait.
\\\\
SUBJECT LINE: CONFIDENTIAL
FROM: Ken Okon[mintlion183@mmail.red]
\\
I am Doctor Ken Okon.
I am the personal attorney to Mr. Tony, a national of your country, who used to work with the Shell Oil Producing Company
Herein after he will be referred to as my client.
On the day of 27th of April, 1970, my client and his wife and their only daughter were contracted a deadly disease and died.
\\
Since then I have made several inquiries to your embassy here to locate any of my client's extended relatives, Which has also proved abbortive.
After these unsuccessful attempts, I decided contact you since you have the same last name.
I have contacted you to assist in repatriating the fund valued at 1350 tonnes of plastic Left behind by my client before it get confiscated or declared unservicable by Plunder \& Flee Incorporated, where this huge amount was deposited.
\\
What bothers me most is the fund, which according to my country's constitution becomes the governments own, if there is no{-}one close to the deceased to claim the funds.
Plunder \& Flee Incorporated have issued me a notice to provide a next of kin or have the account confiscated in the next one month.
For the fact that I have been unsuccessful in locating any relatives of my late client since then, I hereby seek your consent to present yuo as the next{-}of{-}kin to the deceased so that the proceeds of this account can be paid to you.
Therefore, on receipt of your positive response, we shall then discuss the percentage that is comming to me after the money has been credited and the modalities for sharing is as follows: 37\% to me, and the rest to you.
\\
I can assist in procuring the necessary information and legal documents that may be needed to actualise this proposal.
All I requrie from you is your honest coo{-}peration to enable us see this transaction through.
I guarnatee this will be executted under a legitimate platform that will protect you from any breach of law.
\\
I look forward to hear from you soonest.
Please note that this transaction must remain confidential at all times.
Regards, Doctor Ken Okon
\\\\
Jane thinks that this guy is really virtuous, and sends him some money.
John receives 440 Elevated Bills, and is pleased with his gain.
\subsection{A Timeline In Which Jane Is A Call Girl, And John Is Her Customer}


The brothel has a cobalt wood floor, and the walls are painted pink.
Jane's personal serving{-}room has a acacia bed, with aquamarine violet petals strewn about it.
Jane is dressed in a blue babydoll made from silk.
John pays Jane 210 Ebony Notes.
John flosses her cream furniture.
Jane shouts in atrocious bliss, and John continues throughout the night...
\subsection{A Timeline In Which John Drugs Jane}


John pulls out a small aquamarine packet from his pocket. Inside is one of his favourite (although illicit) drugs.
The drug? None other than tretinoprazole, one of the most expensive drugs on the black market.
John quickly dumps the powder into Jane's Pina Colada.
Jane finishes off the rest of her drink, unaware of its extra ingredient.
Shortly afterwards, Jane feels dizzy, but it passes.
More dangerously, however, she is rendered persuadable, which is exactly as John wants her...
\section{The End}
And so, after looking through innumerable timelines, we come to this.
 The end.
 Well, not quite.
There are still innumerable timelines to explore.


But we've run out of time.
So long, folks!
\end{document}